---
title: "copilot_demo"
output: html_document
date: "2025-03-21"
---

## Import libraries
```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
library(readr)
library(reshape2)
library(psych)
```

## Load data

Load the daily report data

```{r}

copilot_demo_df <- read.csv("/Users/adityaponnada/Downloads/time_study_data/sample.csv", header=TRUE)

```

Next, we will get the names pof all the columns
```{r}
colnames(copilot_demo_df)
```

## Data Exploration
Let's take a look at different SCREEN_STATUS types in this dataframe. We will print the frequencies of each of the screen status type. 
```{r}

table(copilot_demo_df$SCREEN_STATUS)
```

## Date manipulation
Next, we will create a new column prompt_ema. This column has two levels EMA, NOT_EMA It is EMA if prompt type is EMA_Micro, or else it is NOT_EMA
```{r}
copilot_demo_df$prompt_ema <- ifelse(copilot_demo_df$Prompt_Type == "EMA_Micro", "EMA", "NOT_EMA")
```

Summarize the frequency of prompt_ema column
```{r}
table(copilot_demo_df$prompt_ema)
```


## T-test
Next we will dfo a t test with prompt_ema as independent variable and LAST_USAGE_DURATION as dependent variable
```{r}
t.test(LAST_USAGE_DURATION ~ prompt_ema, data = copilot_demo_df)
```

## Visualization
Next, we will plot a box-whiskers plot with prompt_ema on x axis and LAST_USAGE_DURATION on y axis. Also we will add a mean line to the boxes.
```{r}


ggplot(copilot_demo_df, aes(x = prompt_ema, y = LAST_USAGE_DURATION)) +
  geom_boxplot() +
  stat_summary(fun = mean, geom = "point", size = 3, color = "red") +
  labs(title = "Boxplot of LAST_USAGE_DURATION by prompt_ema",
       x = "Prompt Type",
       y = "Last Usage Duration") +
  theme_minimal()

```

