---
title: "day_trends_plotting"
output: html_document
date: "2025-04-04"
---

## Import libraries
```{r}
library(lubridate)
library(ggplot2)
library(reshape2)
library(dplyr)
library(psych)
```
## Import data
```{r}

trend_dr_df <- read.csv("/Users/adityaponnada/Downloads/time_study_data/daily_report.csv")

```


## Stitch changed ids together
For some participants the ID was changed. So we merge those rows together
```{r}
trend_dr_df$participant_ID[trend_dr_df$participant_ID == "upliftedsulfatedreamboat@timestudy_com"] <- "startlingrevengevillage@timestudy_com"

trend_dr_df <- subset(trend_dr_df, trend_dr_df$participant_ID != "stephen4_internal@timestudy_com")
trend_dr_df <- subset(trend_dr_df, trend_dr_df$participant_ID != "stephen6_internal@timestudy_com")
```


## Read the watch assignment file
This file is needed to:
1. Filter time dates with uEMA that occurred before the official watch training
2. also filter out the participants that have been unenrolled in the first two bursts before the watch was even assigned

Note: In this file, participant status codes mean:

1=first burst
2=active
3= staff unenrolled
4=participant withdrew
5=competed

```{r}

participant_status_df <- read.csv(file = "/Users/adityaponnada/Downloads/time_study_data/participant_status_tracking_v2.csv", sep = ",", header = TRUE)

# names(participant_status_df) <- c("record_id", "participant_id", "participant_status", "watch_assign_date", "device_tracking")




names(participant_status_df) <- c("record_id", "participant_id", "participant_status", "consent_date", "date_completed", "date_withdrew", "date_unenrolled", "date_device_mailed", "device_id", "watch_assign_date", "exit_interview_date")

participant_status_df$participant_id <- paste0(participant_status_df$participant_id, "@timestudy_com")

```


Remove participants who were never assigned a single watch
```{r}

no_watch_assigned_df <- subset(participant_status_df, participant_status_df$watch_assign_date == "")

no_watch_users = unique(no_watch_assigned_df$participant_id)

```

Keep a dataframe of watch assigned participants
```{r}

watch_users_df <- subset(participant_status_df, participant_status_df$watch_assign_date != "")

```


Convert the watch assignment date into date time stamp or object for future filtering
```{r}

watch_users_df$watch_training_day <- as.POSIXct(watch_users_df$watch_assign_date, format = "%m/%d/%Y")


```


## Filter no watch users
Filter out users who have never been assigned a watch
```{r}

`%!in%` <- Negate(`%in%`)

trend_subset_df <- subset(trend_dr_df, trend_dr_df$participant_ID %!in% no_watch_users)

```

## Convert sleep wake times to date time objects
```{r}

trend_subset_df$current_wake_timestamp <- as.POSIXct(trend_subset_df$current_wake_time, format = "%Y-%m-%d %H:%M:%OS")
trend_subset_df$current_sleep_timestamp <- as.POSIXct(trend_subset_df$current_sleep_time, format = "%Y-%m-%d %H:%M:%OS")

```


## Create a function to filter out user names with less than six months of data in total
We are only looking at the users who have completed at least six months in the study. Thus, we will discard any user who has not completed six months yet
```{r}

keep_six_months_completed <- function(df, num_months){
  num_days = num_months * 30
  # count each 'name', assign result to an object 'tt'
  tt <- table(df$participant_ID)
  # subset data frame by a logical vector
  # 'TRUE' rows are kept, 'FALSE' rows are removed.
  # assign the result to a data frame with a new name
  df2 <- subset(df, df$participant_ID %in% names(tt[tt >= num_days]))
  
  return(df2)
}


```

```{r}
trend_subset_df <- keep_six_months_completed(trend_subset_df, 6)
```



## Remove days with awkward sleep duration due to error
Check summary first
```{r}
trend_subset_df$sleep_time_reported_hr <- as.numeric(trend_subset_df$sleep_time_reported_hr)
```


```{r}
describe(trend_subset_df$sleep_time_reported_hr)

```

Next, assign a day number for each participant, grouped by participant ID and study mode. Use row_number() function for this.
```{r}

trend_subset_df <- trend_subset_df %>% group_by(participant_ID, study_mode) %>% mutate(day_num = row_number())

```


Remove awkward sleep times above 24 hours
```{r}

trend_subset_df <- subset(trend_subset_df, trend_subset_df$sleep_time_reported_hr <= 24.0)
trend_subset_df <- subset(trend_subset_df, trend_subset_df$sleep_time_reported_hr >= 0.0)
```


## Split the dataframe into uEMA and EMA data frames
use TIME and BURST days study mode for separation
```{r}

trend_time_df <- subset(trend_subset_df, trend_subset_df$study_mode == "TIME")
trend_burst_df <- subset(trend_subset_df, trend_subset_df$study_mode == "BURST")

```

keep only watch assigned days and only days after the watch assignment took place
```{r}
trend_time_df <- subset(trend_time_df, trend_time_df$watch_assigned == "True")
```



Only include watch dates after the training date

```{r}

trend_time_df$date_stamp <- as.POSIXct(trend_time_df$date, format = "%Y-%m-%d")

p_ids <- unique(trend_time_df$participant_ID)


for (p_id in p_ids){
  # print(p_id)
  start_date <- watch_users_df$watch_training_day[watch_users_df$participant_id == p_id]
  # print(start_date)
  trend_time_df <- trend_time_df[!(trend_time_df$participant_ID == p_id & trend_time_df$date_stamp <= start_date), ]
  # print(nrow(time_df))
}

```

## Convert prompt counts to numeric
```{r}

trend_time_df$uema_prompted_num <- as.numeric(trend_time_df$uema_prompted_num)
trend_time_df$uema_completed_num <- as.numeric(trend_time_df$uema_completed_num)


```


## Use sleep time reported to get the expected number of uEMA and burst EMA prompts

Rubric to be used:
uEMA num prompts = (24.0 - sleep_time - 0.50)*4.0 --> convert to integer
burst EMA num prompts = (24.0 - sleep_time - 1.0)*1 --> convert to integet

Define the constants
```{r}

uEMA_PER_HOUR = 4.0
EMA_PER_HOUR = 1.0
uEMA_BUFFER_HOUR = 0.5
EMA_BUFFER_HOUR = 1.0

DAY_HOUR = 24.0

```

Compute expected prompts for burst EMA
```{r}


trend_burst_df$burst_ema_expected_num <- as.integer((DAY_HOUR - trend_burst_df$sleep_time_reported_hr - EMA_BUFFER_HOUR)*EMA_PER_HOUR)

```

Compute expected promtps for uEMA
```{r}

trend_time_df$uema_expected_num <- as.integer((DAY_HOUR - trend_time_df$sleep_time_reported_hr - uEMA_BUFFER_HOUR)*uEMA_PER_HOUR)

```

## Convert response rate columns to numeric
In trend_time_df and trend_burst_df, convert the burst_ema_completion_rate and burst_ema_compliance_rate columns to numeric (for trend_burst_df), and convert the uema_completion_rate and uema_compliance_rate columns to numeric (for trend_time_df). Similarly, convert date in both trend_burst_dr, and trend_time_df to POSIXct format in "%Y-%m-%d" format. 

```{r}

trend_burst_df$burst_ema_completion_rate <- as.numeric(trend_burst_df$burst_ema_completion_rate)
trend_burst_df$burst_ema_compliance_rate <- as.numeric(trend_burst_df$burst_ema_compliance_rate)
trend_time_df$uema_completion_rate <- as.numeric(trend_time_df$uema_completion_rate)
trend_time_df$uema_compliance_rate <- as.numeric(trend_time_df$uema_compliance_rate)
trend_burst_df$date_stamp <- as.POSIXct(trend_burst_df$date, format = "%Y-%m-%d")
trend_time_df$date_stamp <- as.POSIXct(trend_time_df$date, format = "%Y-%m-%d")

```

Convert count columns to numeric:
```{r}

trend_burst_df$burst_ema_expected_num <- as.numeric(trend_burst_df$burst_ema_expected_num)
trend_burst_df$burst_ema_original_prompted_num <- as.numeric(trend_burst_df$burst_ema_original_prompted_num)
trend_burst_df$burst_ema_completed_num <- as.numeric(trend_burst_df$burst_ema_completed_num)

trend_time_df$uema_expected_num <- as.numeric(trend_time_df$uema_expected_num)
trend_time_df$uema_prompted_num <- as.numeric(trend_time_df$uema_prompted_num)
trend_time_df$uema_completed_num <- as.numeric(trend_time_df$uema_completed_num)

```

Next, we will set the max for compliance and completion rate columns in trend_time_df and trend_burst_df to 1.0. This means, any compliance or completion rate that is > 1.0 will be set to 1.0.
```{r}

trend_burst_df$burst_ema_completion_rate[trend_burst_df$burst_ema_completion_rate > 1.0] <- 1.0
trend_burst_df$burst_ema_compliance_rate[trend_burst_df$burst_ema_compliance_rate > 1.0] <- 1.0
trend_time_df$uema_completion_rate[trend_time_df$uema_completion_rate > 1.0] <- 1.0
trend_time_df$uema_compliance_rate[trend_time_df$uema_compliance_rate > 1.0] <- 1.0

```

Next, let's assign a day number for each participant in sequency. This is for both trend_time_df and trend_burst_df. 
```{r}
# trend_time_df <- trend_time_df %>% group_by(participant_ID) %>% mutate(day_num = row_number())
# trend_burst_df <- trend_burst_df %>% group_by(participant_ID) %>% mutate(day_num = row_number())
```



if there are dates to be filtered because of technical malfunction, include that code here
```{r}
## Read the missing data file here
missing_notes_file <- read.csv("/Users/adityaponnada/Downloads/time_study_data/missing_data_notes.csv", sep = ",", header = TRUE)

missing_notes_file <- subset(missing_notes_file, missing_notes_file$ACTION == "EXCLUDE")


# replace empty columns with the same date as the other column

missing_notes_file$START_DATE <- ifelse(missing_notes_file$START_DATE == "", missing_notes_file$END_DATE, missing_notes_file$START_DATE)
missing_notes_file$END_DATE <- ifelse(missing_notes_file$END_DATE == "", missing_notes_file$START_DATE, missing_notes_file$END_DATE)

# Convert to date time objects
missing_notes_file$START_DATE <- as.POSIXct(missing_notes_file$START_DATE, format = "%Y-%m-%d")
missing_notes_file$END_DATE <- as.POSIXct(missing_notes_file$END_DATE, format = "%Y-%m-%d")

missing_notes_file$P_ID <- paste0(missing_notes_file$P_ID, "@timestudy_com")


```

Filter out these dates from the combined daily report file - first the common dates
```{r}

all_pid_row <- subset(missing_notes_file, missing_notes_file$P_ID == "ALL_PARTICIPANTS@timestudy_com")

global_start_date <- all_pid_row$START_DATE
global_end_date <- all_pid_row$END_DATE

trend_burst_df <- trend_burst_df[(trend_burst_df$date_stamp <= global_start_date | trend_burst_df$date_stamp >= global_end_date), ]


```

Filter out other phone exclusion dates for the burst_df
```{r}



filter_exclusion_dates <- function(report_df, missing_df, device){
  missing_df <- subset(missing_df, missing_df$DEVICE == device | missing_df$DEVICE == "BOTH")
  missing_df <- subset(missing_df, missing_df$P_ID != "ALL_PARTICIPANTS@timestudy_com")
  pid_list <- unique(missing_df$P_ID)
  for (pid in pid_list){
    # print(paste0("participant: ", pid))
    missing_pid_subset <- subset(missing_df, missing_df$P_ID == pid)
    # print(nrow(missing_pid_subset))
    for (i in 1:nrow(missing_pid_subset)){
      # print(paste0("i: ", i))
      start_date <- missing_pid_subset$START_DATE[i]
      end_date <- missing_pid_subset$END_DATE[i]
      # print(start_date)
      # print(end_date)
      # print(paste0("nrow before: ", nrow(report_df)))
      test_subset <- subset(report_df, report_df$participant_ID == pid)
      test_subset <- test_subset[(test_subset$date_stamp >= start_date & test_subset$date_stamp <= end_date), ]
      # print(paste0("test_df nrow: ", nrow(test_subset)))
      # print(paste0("row: ", test_subset$date_object))
      report_df <- dplyr::setdiff(report_df, test_subset)
      # report_df <- subset(report_df, !(report_df$participant_ID == pid & report_df$date_object >= start_date) | (report_df$participant_ID == pid & report_df$date_object <= end_date))
      # print(paste0("nrow after: ", nrow(report_df)))
    }
  }
  
  return(report_df)
}


```

Get burst and time df updated
```{r}
# original number of rows 6168

trend_burst_df <- filter_exclusion_dates(trend_burst_df, missing_notes_file, "PHONE")

# original number of rows 13415
trend_time_df <- filter_exclusion_dates(trend_time_df, missing_notes_file, "WATCH")
```

Also check by removing outliers
```{r}

remove_outliers_from_df <- function(df){
  outliers <- c("uniformlyharmfulbush@timestudy_com", "penpalsandbanklifting@timstudy_com")
  df <- subset(df, df$participant_ID %!in% outliers)
  return(df)
}

```

Remove these outliers from both time and burst trend df
```{r}

trend_burst_df <- remove_outliers_from_df(trend_burst_df)
trend_time_df <- remove_outliers_from_df(trend_time_df)

```

Create a separate plotting dataframes for both trend_burst_df and trend_time_df. For trend_bust_df, we will only keep burst compliance and comppletion rate columns, participant_ID, and day_num column. Similarly, for trend_time_df, we will keep the uema_compliance and completion rate columns.
```{r}

trend_burst_plot_df <- trend_burst_df[, c("participant_ID", "day_num", "burst_ema_completion_rate", "burst_ema_compliance_rate")]
trend_time_plot_df <- trend_time_df[, c("participant_ID", "day_num", "uema_completion_rate", "uema_compliance_rate")]

```

Next, we will attach the participant status to these data frames. For this, we will get the status from participant_status for each ID and then add the status column to trend_time_df, and trend_burst_df.
```{r}
trend_burst_plot_df <- merge(trend_burst_plot_df, participant_status_df[, c("participant_id", "participant_status")], by.x = "participant_ID", by.y = "participant_id", all.x = TRUE)
trend_time_plot_df <- merge(trend_time_plot_df, participant_status_df[, c("participant_id", "participant_status")], by.x = "participant_ID", by.y = "participant_id", all.x = TRUE)



```


Make the column names consistent for the plotting dataframes. Basically, they should have participant_ID, day_num, completion_rate, compliance_rate, and status
```{r}

names(trend_burst_plot_df) <- c("participant_ID", "day_num", "completion_rate", "compliance_rate", "participant_status")
names(trend_time_plot_df) <- c("participant_ID", "day_num", "completion_rate", "compliance_rate", "participant_status")

```


Create a new dataframe with only the earliest day number from trend_time_plot_df
```{r}
trend_time_plot_df_earliest <- trend_time_plot_df %>% group_by(participant_ID) %>% filter(day_num == min(day_num)) %>% ungroup()
```

Summarize the day_num for trend_time_plot_df_earliest. Also get the 25th and 75th percentiles for the day_num column. This will give us the number of days it took for the data collection to start.
```{r}

describe(trend_time_plot_df_earliest$day_num)
IQR(trend_time_plot_df_earliest$day_num)
quantile(trend_time_plot_df_earliest$day_num, c(0.25, 0.75))

```
Now summarize the same info by participant status. Overall, it takes a median of 15 days for the actual data collection to start.
```{r}

describeBy(trend_time_plot_df_earliest$day_num, group = trend_time_plot_df_earliest$participant_status)

```


## Plot the seasonality plot for compliance and completion rate
basically a facet of participant status 3 columns, each plot EMA compliance and completion rates
```{r}


plot_seasonality_ema <- function(df, status_type){
  
  df <- subset(df, df$participant_status == status_type)
  
  to_keep <- c("day_num", "compliance_rate", "completion_rate")
  df <- df[, to_keep]
  
  df <- reshape2::melt(df, id.var='day_num')
  
  line_plot <- ggplot(data=df, aes(x=day_num, y=value, color = variable)) +
    # geom_line(size = 1) +
    # geom_point() +
    theme_bw() +
    scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.5)) +
    scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, by = 50)) +
    # scale_x_discrete(labels = c("Home", "School", "Work", "Friend", "Unlabeled", "Transit", "Other")) +
    # theme(axis.text.x = element_text(angle = 45, margin = margin(t = 5))) +
    # stat_summary(geom="ribbon", fun.data=mean_cl_normal, conf.int=0.95, fill="lightblue", alpha = 0.5) +
    # stat_summary(fun.y = mean, geom = "line", aes(ymax= ..y.., ymin = ..y..),
    #            width = 0.1, size = 1) +
    geom_smooth(method='gam') +
    # scale_colour_manual("", values = c(Compliance = "blue", Completion = "red")) +
    # scale_y_continuous(breaks = c(0, 0.5, 1.0), label = c("0", "0.5", "1.0")) +
    labs(x = "Days in study", y = "Rate", color = "Rate type") +
    scale_color_manual(labels = c("Compliance rate", "Completion rate"), values = c("red", "blue")) +
    theme(axis.title = element_text(size = 15), axis.text.x = element_text(size = 15, colour = "black"), axis.text.y = element_text(size = 15, colour = "black"), title = element_text(size = 15), axis.title.x=element_blank(), legend.text = element_text(size = 15)) +
    ggtitle(status_type) +
    theme(
    legend.position = c(0.25, 0.15)
    # panel.grid.major.y = element_line(c(0, 25, 50, 75, 100),
    #   color = "#D9D9D9",
    #   size = 15)
  ) +
    guides(colour = guide_legend(nrow = 2))
  
  return(line_plot)
  
}

```


```{r}
plot_seasonality_uema <- function(df, status_type){
  
  df <- subset(df, df$participant_status == status_type)
  
  to_keep <- c("day_num", "compliance_rate", "completion_rate")
  df <- df[, to_keep]
  
  df <- reshape2::melt(df, id.var='day_num')
  
  line_plot <- ggplot(data=df, aes(x=day_num, y=value, color = variable)) +
    # geom_line(size = 1) +
    # geom_point() +
    theme_bw() +
    scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.5)) +
    scale_x_continuous(limits = c(0, 260), breaks = seq(0, 260, by = 130)) +
    # scale_x_discrete(labels = c("Home", "School", "Work", "Friend", "Unlabeled", "Transit", "Other")) +
    # theme(axis.text.x = element_text(angle = 45, margin = margin(t = 5))) +
    # stat_summary(geom="ribbon", fun.data=mean_cl_normal, conf.int=0.95, fill="lightblue", alpha = 0.5) +
    # stat_summary(fun.y = mean, geom = "line", aes(ymax= ..y.., ymin = ..y..),
    #            width = 0.1, size = 1) +
    geom_smooth(method="gam") +
    # scale_colour_manual("", values = c(Compliance = "blue", Completion = "red")) +
    # scale_y_continuous(breaks = c(0, 0.5, 1.0), label = c("0", "0.5", "1.0")) +
    labs(x = "Days in study", y = "Rate", color = "Rate type") +
    scale_color_manual(labels = c("Compliance rate", "Completion rate"), values = c("red", "blue")) +
    theme(axis.title = element_text(size = 15), axis.text.x = element_text(size = 15, colour = "black"), axis.text.y = element_text(size = 15, colour = "black"), title = element_text(size = 15), axis.title.x=element_blank(), legend.text = element_text(size = 15)) +
    ggtitle(status_type) +
    theme(
    legend.position = c(0.25, 0.15)
    # panel.grid.major.y = element_line(c(0, 25, 50, 75, 100),
    #   color = "#D9D9D9",
    #   size = 15)
  ) +
    guides(colour = guide_legend(nrow = 2))
  
  return(line_plot)
  
}
```


## Plot to get number of participants per day
```{r}

plot_num_part_days <- function(df, type, status_type){
  
  if (type == "uema"){
    max_limit = 260
    day_type = "µEMA"
    
  } else if (type == "ema"){
    max_limit = 100
    day_type = "EMA"
  }
  
  split_val = max_limit/2
  
  df <- subset(df, df$participant_status == status_type)
  
  
  keep_names <- c("participant_ID", "day_num")
  df <- df[, keep_names]
  
  # df <- df %>% group_by(participant_ID) %>% mutate(actual_days = row_number())
  # 
  # 
  # df <- df[, c("participant_ID", "actual_days")]
  
  
  # agg_df <- distinct(df)
  
  agg_df <- aggregate(df$day_num, by = list(df$day_num), FUN = length)
  names(agg_df) <- c("Days", "Num_Ps")
  
  agg_df$Days <- as.numeric(agg_df$Days)
  
  # agg_df <- summarise(group_by(df,Participant_ID, EXPOSURE_DAY_NO),length(Participant_ID))
  # names(agg_df) <- c("Participant_ID", "max_expo_day", "COUNT")
  # 
  # agg_df <- agg_df %>%
  # group_by(Participant_ID, max_expo_day) %>%
  # mutate(COMPLETION_RATE = COUNT / sum(COUNT))
  # 
  # agg_df <- subset(agg_df, agg_df$ANSWER_STATUS == "Answered")
  # 
  # agg_df$max_expo_day <- as.numeric(agg_df$max_expo_day)
  # 
  line_plot <- ggplot(data=agg_df) +
    # geom_line(aes(x=Days, y=Num_Ps), size = 1) +
    geom_smooth(method='gam', aes(x=Days, y=Num_Ps), color='black') + 
    # geom_point() +
    theme_bw() +
    scale_y_continuous(limits = c(0, 150), breaks = seq(0, 150, by = 50)) +
    scale_x_continuous(limits = c(0, max_limit), breaks = seq(0, max_limit, by = split_val)) +
    # scale_x_discrete(labels = c("Home", "School", "Work", "Friend", "Unlabeled", "Transit", "Other")) +
    # theme(axis.text.x = element_text(angle = 45, margin = margin(t = 5))) +
    # stat_summary(geom="ribbon", fun.data=mean_cl_normal, conf.int=0.95, fill="lightblue", alpha = 0.5) +
    # stat_summary(fun.y = mean, geom = "line", aes(ymax= ..y.., ymin = ..y..),
    #            width = 0.1, size = 1) +
    # scale_y_continuous(breaks = c(0, 0.5, 1.0), label = c("0", "0.5", "1.0")) +
    labs(x = paste0(day_type, " days"), y = "No. participants") +
    theme(axis.title = element_text(size = 15), axis.text.x = element_text(size = 15, colour = "black"), axis.text.y = element_text(size = 15, colour = "black"), title = element_text(size = 15)) 
  # + ggtitle(paste0(day_type, " ", status_type))
   
  
   # ylim(0, 1) +
    # xlim(0, 300)
  
  # box_plot <- ggplot(agg_df, aes(x=DAYS_IN_THE_STUDY, y=COMPLETION_RATE)) + 
  # geom_boxplot() +
  #   ggtitle("Completion | Days in the study")
  # 
  # summary_object <- describeBy(agg_df$COMPLETION_RATE, group = agg_df$DAYS_IN_THE_STUDY)
  # 
  # print(summary_object)
  
  # return_list <- c(summary_object, box_plot)
  
  return(line_plot)
}

```

## Put the plots together
```{r}

library(ggpubr)

uema_com_plot <- plot_seasonality_uema(trend_time_plot_df, "Completed")
uema_wdr_plot <- plot_seasonality_uema(trend_time_plot_df, "Withdrew")
uema_unen_plot <- plot_seasonality_uema(trend_time_plot_df, "Unenrolled")

ema_com_plot <- plot_seasonality_ema(trend_burst_plot_df, "Completed")
ema_wdr_plot <- plot_seasonality_ema(trend_burst_plot_df, "Withdrew")
ema_unen_plot <- plot_seasonality_ema(trend_burst_plot_df, "Unenrolled")

uema_num_com <- plot_num_part_days(trend_time_plot_df, "uema", "Completed")
uema_num_wdr <- plot_num_part_days(trend_time_plot_df, "uema", "Withdrew")
uema_num_unen <- plot_num_part_days(trend_time_plot_df, "uema", "Unenrolled")

ema_num_com <- plot_num_part_days(trend_burst_plot_df, "ema", "Completed")
ema_num_wdr <- plot_num_part_days(trend_burst_plot_df, "ema", "Withdrew")
ema_num_unen <- plot_num_part_days(trend_burst_plot_df, "ema", "Unenrolled")


uema_arranged <- ggarrange(uema_com_plot, uema_wdr_plot, uema_unen_plot, uema_num_com, uema_num_wdr, uema_num_unen, ncol = 3, nrow = 2)

ema_arranged <- ggarrange(ema_com_plot, ema_wdr_plot, ema_unen_plot, ema_num_com, ema_num_wdr, ema_num_unen, ncol = 3, nrow = 2)

```