---
title: "perceived_burden_parsing"
author: "Aditya Ponnada"
date: "7/7/2021"
output: html_document
---

## import libraries
```{r}

library(ggplot2)
library(psych)
library(reshape2)
library(dplyr)
library(lsr)


```

## Read in the burden file
```{r}


perceived_burden_data <- read.csv(file = "D:/uema_ema_comparison_CHI/perceived_burden/TIMEMAIN-AdityaBurden_DATA_2021-07-07_1126.csv", sep = ",", header = TRUE)

```


## Split into 6m and exit survey dfs

First, get the column names and then split column names into two
```{r}

all_col_names <- names(perceived_burden_data)

```

Get column names for 6 months survey
```{r}

common_cols <- c(1:3)
six_mon_cols <- c(4:52)
exit_cols <- c(53:112)

id_df <-perceived_burden_data[, common_cols]
six_mon_df <- perceived_burden_data[, six_mon_cols]
exit_df <- perceived_burden_data[, exit_cols]


```

Stitch the id columns to other dataframes
```{r}

six_mon_df <- cbind(id_df, six_mon_df)
exit_df <- cbind(id_df, exit_df)


```

keep only perceived burden scale related columns
```{r}

remove_six_mon_cols <- c(c(25:27), c(49:52))
remove_exit_cols <- c(c(25:33), c(55:63))


```

Remove these column names from the dataframes
```{r}

six_mon_df <- six_mon_df %>% select(-remove_six_mon_cols)

exit_df <- exit_df %>% select(-remove_exit_cols)

```

## Remove non exit survey users

Remove users who have not completed the exit survey
This is because either they are still active or they just did not fill it

```{r}

exit_df <- exit_df[!apply(is.na(exit_df[,4:45]), 1, all),]

```

Do the same for six months dataframe
```{r}

six_mon_df <- six_mon_df[!apply(is.na(six_mon_df[,4:45]), 1, all),]

```

## Rename columns in exit to match with 6 months
```{r}

exit_cols <- names(exit_df)

new_exit_cols <- c()

for (col_name in exit_cols){
  
  
  if (grepl( "engagement", col_name, fixed = TRUE)) {
    col_name <- gsub("_exit", "", col_name)
  }
  
  new_exit_cols <- c(new_exit_cols, col_name)
  
}

names(exit_df) <- new_exit_cols

```

## Rename column names for the dataframes
First read the mapping file
```{r}
q_id_map_df <- read.csv(file="D:/uema_ema_comparison_CHI/perceived_burden/question_id_mapping.csv", sep=",", header=TRUE)

q_id_map_df$device_subscale_id <- paste0(q_id_map_df$Device, "_", q_id_map_df$Subscale_ID)

current_qid_list <- q_id_map_df$Q_ID
subscale_id_list <- q_id_map_df$device_subscale_id




```

Rename columnn names for the six months and exit survey
```{r}

subscale_id_list <- c("record_id", "visualizerid", "participant_status", c(subscale_id_list))

names(six_mon_df) <- subscale_id_list
names(exit_df) <- subscale_id_list


```

## Add total and subscale scores
first, create a common function
```{r}

compute_total_burden <- function(df){
  phone_burden_col = names(df)[c(c(4:20), c(23, 24))]
  watch_burden_col = names(df)[c(c(25:41), c(44, 45))]
  df$total_phone_burden <- rowSums(df[,phone_burden_col], na.rm = TRUE)
  df$total_watch_burden <- rowSums(df[,watch_burden_col], na.rm = TRUE)
  
  return(df)
  
}

```

Then assign new columns to exit and six month surveys
```{r}

exit_df <- compute_total_burden(exit_df)
six_mon_df <- compute_total_burden(six_mon_df)


```

## Now add inidividual burden subscale scores
```{r}

add_subscale_burden <- function(df){
 
  
  difficult_burden = c("difficult_1", "difficult_2", "difficult_3", "difficult_4")
  physical_burden = c("physical_1", "physical_2")
  timesocial_burden = c("timesocial_1", "timesocial_2", "timesocial_3", "timesocial_4")
  cognitive_burden = c("cognitive_1", "cognitive_2", "cognitive_3", "cognitive_4", "cognitive_5", "cognitive_6")
  interruption_burden = c("interrupt_1", "interrupt_2", "interrupt_3")
  engagement = c("engagement_1", "engagement_2")
  
  difficult_burden_watch <- paste0("watch_", difficult_burden)
  physical_burden_watch <- paste0("watch_", physical_burden)
  timesocial_burden_watch <- paste0("watch_", timesocial_burden)
  cognitive_burden_watch <- paste0("watch_", cognitive_burden)
  interruption_burden_watch <- paste0("watch_", interruption_burden)
  engagement_watch <- paste0("watch_", engagement)
  
  difficult_burden_phone <- paste0("phone_", difficult_burden)
  physical_burden_phone <- paste0("phone_", physical_burden)
  timesocial_burden_phone <- paste0("phone_", timesocial_burden)
  cognitive_burden_phone <- paste0("phone_", cognitive_burden)
  interruption_burden_phone <- paste0("phone_", interruption_burden)
  engagement_phone <- paste0("phone_", engagement)
  
  df$difficult_burden_phone <- rowSums(df[,difficult_burden_phone], na.rm = TRUE)
  df$physical_burden_phone <- rowSums(df[,physical_burden_phone], na.rm = TRUE)
  df$timesocial_burden_phone <- rowSums(df[,timesocial_burden_phone], na.rm = TRUE)
  df$cognitive_burden_phone <- rowSums(df[,cognitive_burden_phone], na.rm = TRUE)
  df$interruption_burden_phone <- rowSums(df[,interruption_burden_phone], na.rm = TRUE)
  df$engagement_phone <- rowSums(df[,engagement_phone], na.rm = TRUE)
  
  df$difficult_burden_watch <- rowSums(df[,difficult_burden_watch], na.rm = TRUE)
  df$physical_burden_watch <- rowSums(df[,physical_burden_watch], na.rm = TRUE)
  df$timesocial_burden_watch <- rowSums(df[,timesocial_burden_watch], na.rm = TRUE)
  df$cognitive_burden_watch <- rowSums(df[,cognitive_burden_watch], na.rm = TRUE)
  df$interruption_burden_watch <- rowSums(df[,interruption_burden_watch], na.rm = TRUE)
  df$engagement_watch <- rowSums(df[,engagement_watch], na.rm = TRUE)
  
  return(df)
  
  
   
}

```

Now apply this function to the exit and 6m df
```{r}

exit_df <- add_subscale_burden(exit_df)
six_mon_df <- add_subscale_burden(six_mon_df)

```


## Describe burden and engagement variables
```{r}

# Remove temporarily
# six_mon_df <- subset(six_mon_df, six_mon_df$total_watch_burden != 0)

```

List descriptives here for six months df
```{r}

describe(six_mon_df$total_phone_burden)
describe(six_mon_df$total_watch_burden)

describe(six_mon_df$difficult_burden_phone)
describe(six_mon_df$difficult_burden_watch)

describe(six_mon_df$timesocial_burden_phone)
describe(six_mon_df$timesocial_burden_watch)

describe(six_mon_df$physical_burden_phone)
describe(six_mon_df$physical_burden_watch)

describe(six_mon_df$cognitive_burden_phone)
describe(six_mon_df$cognitive_burden_watch)

describe(six_mon_df$interruption_burden_phone)
describe(six_mon_df$interruption_burden_watch)

describe(six_mon_df$engagement_phone)
describe(six_mon_df$engagement_watch)


```

## Plot distributions for six months data
plot overall burden distribution - phone
```{r}


mean_burden = mean(six_mon_df$total_phone_burden)
median_burden = median(six_mon_df$total_phone_burden)

phone_burden_plot <- ggplot(six_mon_df, aes(x=total_phone_burden)) + 
  geom_histogram() +
  ggtitle("Total burden EMA") +
  geom_vline(aes(xintercept = mean(total_phone_burden)), data=six_mon_df, linetype=5, color = "red") +
  geom_vline(aes(xintercept = median(total_phone_burden)), data=six_mon_df, linetype=5, color = "green") +
  geom_text(aes(x=mean_burden, label=paste0("\nmean = ", format(round(mean_burden, 2), nsmall = 2)), y=8), colour="black", angle=90, text=element_text(size=20)) +
  geom_text(aes(x=median_burden, label=paste0("\nmed = ", format(round(median_burden, 2), nsmall = 2)), y=4), colour="black", angle=90, text=element_text(size=20)) +
  ylim(0, 15) +
  xlim(19,95)


```

plot overall burden distribution - watch
```{r}


mean_burden = mean(six_mon_df$total_watch_burden)
median_burden = median(six_mon_df$total_watch_burden)

watch_burden_plot <- ggplot(six_mon_df, aes(x=total_watch_burden)) + 
  geom_histogram() +
  ggtitle("Total burden uEMA") +
  geom_vline(aes(xintercept = mean(total_watch_burden)), data=six_mon_df, linetype=5, color = "red") +
  geom_vline(aes(xintercept = median(total_watch_burden)), data=six_mon_df, linetype=5, color = "green") +
  geom_text(aes(x=mean_burden, label=paste0("\nmean = ", format(round(mean_burden, 2), nsmall = 2)), y=8), colour="black", angle=90, text=element_text(size=20)) +
  geom_text(aes(x=median_burden, label=paste0("\nmed = ", format(round(median_burden, 2), nsmall = 2)), y=4), colour="black", angle=90, text=element_text(size=20)) +
  ylim(0, 15) +
  xlim(19,95)


```


## Plot engagement plot for watch and phone

For phone
```{r}

mean_engagement = mean(six_mon_df$engagement_phone)
median_engagement = median(six_mon_df$engagement_phone)

phone_engagement_plot <- ggplot(six_mon_df, aes(x=engagement_phone)) + 
  geom_histogram() +
  ggtitle("Engagement EMA") +
  geom_vline(aes(xintercept = mean(engagement_phone)), data=six_mon_df, linetype=5, color = "red") +
  geom_vline(aes(xintercept = median(engagement_phone)), data=six_mon_df, linetype=5, color = "green") +
  geom_text(aes(x=mean_engagement, label=paste0("\nmean = ", format(round(mean_engagement, 2), nsmall = 2)), y=8), colour="black", angle=90, text=element_text(size=20)) +
  geom_text(aes(x=median_engagement, label=paste0("\nmed = ", format(round(median_engagement, 2), nsmall = 2)), y=4), colour="black", angle=90, text=element_text(size=20)) +
  ylim(0, 20) +
  xlim(2,12)




```

For watch
```{r}

mean_engagement = mean(six_mon_df$engagement_watch)
median_engagement = median(six_mon_df$engagement_watch)

watch_engagement_plot <- ggplot(six_mon_df, aes(x=engagement_watch)) + 
  geom_histogram() +
  ggtitle("Engagement EMA") +
  geom_vline(aes(xintercept = mean(engagement_watch)), data=six_mon_df, linetype=5, color = "red") +
  geom_vline(aes(xintercept = median(engagement_watch)), data=six_mon_df, linetype=5, color = "green") +
  geom_text(aes(x=mean_engagement, label=paste0("\nmean = ", format(round(mean_engagement, 2), nsmall = 2)), y=8), colour="black", angle=90, text=element_text(size=20)) +
  geom_text(aes(x=median_engagement, label=paste0("\nmed = ", format(round(median_engagement, 2), nsmall = 2)), y=4), colour="black", angle=90, text=element_text(size=20)) +
  ylim(0, 20) +
  xlim(2,12)




```


List descriptives here for exit df
```{r}

describe(exit_df$total_phone_burden)
describe(exit_df$total_watch_burden)

describe(exit_df$difficult_burden_phone)
describe(exit_df$difficult_burden_watch)

describe(exit_df$timesocial_burden_phone)
describe(exit_df$timesocial_burden_watch)

describe(exit_df$physical_burden_phone)
describe(exit_df$physical_burden_watch)

describe(exit_df$cognitive_burden_phone)
describe(exit_df$cognitive_burden_watch)

describe(exit_df$interruption_burden_phone)
describe(exit_df$interruption_burden_watch)

describe(exit_df$engagement_phone)
describe(exit_df$engagement_watch)


```

## Plot burden distributions for exit df
For phone
```{r}


mean_exit_burden = mean(exit_df$total_phone_burden)
median_exit_burden = median(exit_df$total_phone_burden)

phone_exit_burden_plot <- ggplot(exit_df, aes(x=total_phone_burden)) + 
  geom_histogram() +
  ggtitle("Total burden EMA | Exit") +
  geom_vline(aes(xintercept = mean(total_phone_burden)), data=exit_df, linetype=5, color = "red") +
  geom_vline(aes(xintercept = median(total_phone_burden)), data=exit_df, linetype=5, color = "green") +
  geom_text(aes(x=mean_exit_burden, label=paste0("\nmean = ", format(round(mean_exit_burden, 2), nsmall = 2)), y=4), colour="black", angle=90, text=element_text(size=20)) +
  geom_text(aes(x=median_exit_burden, label=paste0("\nmed = ", format(round(median_exit_burden, 2), nsmall = 2)), y=2), colour="black", angle=90, text=element_text(size=20)) +
  ylim(0, 5) +
  xlim(19,95)



```

For watch
```{r}


mean_exit_burden = mean(exit_df$total_watch_burden)
median_exit_burden = median(exit_df$total_watch_burden)

watch_exit_burden_plot <- ggplot(exit_df, aes(x=total_watch_burden)) + 
  geom_histogram() +
  ggtitle("Total burden uEMA | Exit") +
  geom_vline(aes(xintercept = mean(total_watch_burden)), data=exit_df, linetype=5, color = "red") +
  geom_vline(aes(xintercept = median(total_watch_burden)), data=exit_df, linetype=5, color = "green") +
  geom_text(aes(x=mean_exit_burden, label=paste0("\nmean = ", format(round(mean_exit_burden, 2), nsmall = 2)), y=4), colour="black", angle=90, text=element_text(size=20)) +
  geom_text(aes(x=median_exit_burden, label=paste0("\nmed = ", format(round(median_exit_burden, 2), nsmall = 2)), y=2), colour="black", angle=90, text=element_text(size=20)) +
  ylim(0, 5) +
  xlim(19,95)



```

## Combine the Exit and 6months for common participants
```{r}

exit_users <- unique(exit_df$visualizerid)

six_mon_exit_df <- subset(six_mon_df, six_mon_df$visualizerid %in% exit_users)

new_exit_df <- exit_df

# names(new_exit_df) <- paste0(names(new_exit_df), "_exit")

## Temporarily remove the exit user who has not filled out six months survey completely

```

# Cbind them or merge them
```{r}

common_df <- merge(six_mon_exit_df, new_exit_df, by.x = "visualizerid", by.y = "visualizerid", all.x = TRUE, all.y = TRUE)

```

get a smaller df with only total burden and engagement scales with user ids

```{r}


keep_cols <- c("visualizerid", "total_phone_burden.x", "total_phone_burden.y", "total_watch_burden.x", "total_watch_burden.y", "engagement_phone.x", "engagement_phone.y", "engagement_watch.x", "engagement_watch.y")

common_col_df <- common_df[, keep_cols]

names(common_col_df) <- c("p_id", "phone_burden_6m", "phone_burden_exit", "watch_burden_6m", "watch_burden_exit", "engagement_phone_6m", "engagement_phone_exit", "engagement_watch_6m", "engagement_watch_exit")

```

box plot before after
```{r}

get_box_plot_pairs <- function(df, col1, col2, min_val, max_val){
  keep <- c("p_id",col1, col2)
  df <- df[, keep]
  df_long <- melt(df, measure.vars = c(col1, col2))
  plot_title <- gsub("_6m", "", col1)
  
  gplot <- ggplot(df_long, aes(x = variable, y = value, colour = p_id)) +
    geom_point() +
    geom_line(aes(group = p_id)) +
    stat_summary(
    geom = "point",
    fun.y = "mean",
    col = "black",
    size = 3,
    fill = "black") +
    stat_summary(aes(y = value,group=1), fun.y=mean, colour="black", geom="line",group=1) +
    ggtitle(paste0("Change in ", plot_title)) +
    ylim(min_val, max_val)
  
  
  return(gplot)
  
}

```

Get phone burden change plot
```{r}

phone_burden_change <- get_box_plot_pairs(common_col_df, "phone_burden_6m", "phone_burden_exit", 19, 95)

```

Get watch burden change plot
```{r}

watch_burden_change <- get_box_plot_pairs(common_col_df, "watch_burden_6m", "watch_burden_exit", 19, 95)

```

Get phone engagement plot
```{r}


phone_engagement_change <- get_box_plot_pairs(common_col_df, "engagement_phone_6m", "engagement_phone_exit", 2, 10)

```

get watch engagement plot
```{r}

watch_engagement_change <- get_box_plot_pairs(common_col_df, "engagement_watch_6m", "engagement_watch_exit", 2, 10)

```


## Compare six months burden statistically
using paired samples t-test
```{r}

t.test(six_mon_df$total_phone_burden, six_mon_df$total_watch_burden, paired = TRUE, alternative = "two.sided")

```

Compute effect sizes
```{r}

total_burdn_long_df <- six_mon_df[, c("visualizerid", "total_phone_burden", "total_watch_burden")]

total_burdn_long_df <-melt(total_burdn_long_df, id.vars=c("visualizerid"))

# cohen.d(six_mon_df$total_phone_burden, six_mon_df$total_watch_burden)

cohensD(value~variable, data = total_burdn_long_df) 


```

Compare engagement statistically
```{r}

t.test(six_mon_df$engagement_phone, six_mon_df$engagement_watch, paired = TRUE, alternative = "two.sided")

```

Compute effect sizes
```{r}

total_engagement_long_df <- six_mon_df[, c("visualizerid", "engagement_phone", "engagement_watch")]

total_engagement_long_df <-melt(total_engagement_long_df, id.vars=c("visualizerid"))

# cohen.d(six_mon_df$total_phone_burden, six_mon_df$total_watch_burden)

cohensD(value~variable, data = total_engagement_long_df) 

```

