---
title: "tochi_submission"
author: "Aditya Ponnada"
date: '2022-09-17'
output: html_document
---

## Import libraries
```{r}

library(psych)
library(reshape2)
library(ggplot2)
library(plyr)
library(dplyr)
library(plotly)
options(digits = 4)
options(digits.secs = 3)
library(corrplot)
library(lme4)

```

## Read and combine the report files
Read all the report files and combine them into one data frame for analysis
```{r}

# report_file_loc = "D:/TIME_CLUSTER_PREPROCESSED_20210702/daily_report/"
# 
# file_pattern <- paste0(report_file_loc, '*@timestudy_com.csv')
# 
# file_matches <- Sys.glob(file_pattern)
# 
# daily_report_df <- do.call(rbind, lapply(file_matches, read.csv))

# daily_report_df <- read.csv("E:/SHARED_GLOBUS_DATA/Combined_daily_report/combined_report_1634336199.8833838.csv")
daily_report_df <- read.csv("/Users/adityaponnada/Downloads/time_study_data/daily_report.csv")

```

## Stitch changed ids together
For some participants the ID was changed. So we merge those rows together
```{r}
daily_report_df$participant_ID[daily_report_df$participant_ID == "upliftedsulfatedreamboat@timestudy_com"] <- "startlingrevengevillage@timestudy_com"

daily_report_df <- subset(daily_report_df, daily_report_df$participant_ID != "stephen4_internal@timestudy_com")
daily_report_df <- subset(daily_report_df, daily_report_df$participant_ID != "stephen6_internal@timestudy_com")
```


## Read the watch assignment file
This file is needed to:
1. Filter time dates with uEMA that occurred before the official watch training
2. also filter out the participants that have been unenrolled in the first two bursts before the watch was even assigned

Note: In this file, participant status codes mean:

1=first burst
2=active
3= staff unenrolled
4=participant withdrew
5=competed

```{r}

participant_status_df <- read.csv(file = "/Users/adityaponnada/Downloads/time_study_data/participant_status_tracking_v2.csv", sep = ",", header = TRUE)

# names(participant_status_df) <- c("record_id", "participant_id", "participant_status", "watch_assign_date", "device_tracking")




names(participant_status_df) <- c("record_id", "participant_id", "participant_status", "consent_date", "date_completed", "date_withdrew", "date_unenrolled", "date_device_mailed", "device_id", "watch_assign_date", "exit_interview_date")

participant_status_df$participant_id <- paste0(participant_status_df$participant_id, "@timestudy_com")

```


Remove participants who were never assigned a single watch
```{r}

no_watch_assigned_df <- subset(participant_status_df, participant_status_df$watch_assign_date == "")

no_watch_users = unique(no_watch_assigned_df$participant_id)

```

Keep a dataframe of watch assigned participants
```{r}

watch_users_df <- subset(participant_status_df, participant_status_df$watch_assign_date != "")

```


Convert the watch assignment date into date time stamp or object for future filtering
```{r}

watch_users_df$watch_training_day <- as.POSIXct(watch_users_df$watch_assign_date, format = "%m/%d/%Y")


```


## Filter no watch users
Filter out users who have never been assigned a watch
```{r}

`%!in%` <- Negate(`%in%`)

daily_report_subset <- subset(daily_report_df, daily_report_df$participant_ID %!in% no_watch_users)

```


## Get a distribution of the study duration for withdrawn, completed, and unenrolled participants

Take a difference between the start date and the completed vs unenrolled vs withdrawn date
```{r}


watch_users_df$STUDY_START <- as.POSIXct(watch_users_df$consent_date, format = "%m/%d/%Y")
watch_users_df$STUDY_COMPLETED <- as.POSIXct(watch_users_df$date_completed, format = "%m/%d/%Y")
watch_users_df$STUDY_WITHDRAW <- as.POSIXct(watch_users_df$date_withdrew, format = "%m/%d/%Y")
watch_users_df$STUDY_UNENROLL <- as.POSIXct(watch_users_df$date_unenrolled, format = "%m/%d/%Y")

watch_users_df$DUR_COMPLETED <- as.numeric(difftime(watch_users_df$STUDY_COMPLETED, watch_users_df$STUDY_START, units = "days"))

watch_users_df$DUR_WITHDRAW <- as.numeric(difftime(watch_users_df$STUDY_WITHDRAW, watch_users_df$STUDY_START, units = "days"))

watch_users_df$DUR_UNENROLL <- as.numeric(difftime(watch_users_df$STUDY_UNENROLL, watch_users_df$STUDY_START, units = "days"))

```

Plot the distributions for unenrolled, withdrew and completed study durations
```{r}

hist(watch_users_df$DUR_COMPLETED)
hist(watch_users_df$DUR_WITHDRAW)
hist(watch_users_df$DUR_UNENROLL)


```

## Convert sleep wake times to date time objects
```{r}

daily_report_subset$current_wake_timestamp <- as.POSIXct(daily_report_subset$current_wake_time, format = "%Y-%m-%d %H:%M:%OS")
daily_report_subset$current_sleep_timestamp <- as.POSIXct(daily_report_subset$current_sleep_time, format = "%Y-%m-%d %H:%M:%OS")

```


## Create a function to filter out user names with less than six months of data in total
We are only looking at the users who have completed at least six months in the study. Thus, we will discard any user who has not completed six months yet
```{r}

keep_six_months_completed <- function(df, num_months){
  num_days = num_months * 30
  # count each 'name', assign result to an object 'tt'
  tt <- table(df$participant_ID)
  # subset data frame by a logical vector
  # 'TRUE' rows are kept, 'FALSE' rows are removed.
  # assign the result to a data frame with a new name
  df2 <- subset(df, df$participant_ID %in% names(tt[tt >= num_days]))
  
  return(df2)
}


```

```{r}
daily_report_subset <- keep_six_months_completed(daily_report_subset, 6)
```



## Remove days with awkward sleep duration due to error
Check summary first
```{r}
daily_report_subset$sleep_time_reported_hr <- as.numeric(daily_report_subset$sleep_time_reported_hr)
```


```{r}
describe(daily_report_subset$sleep_time_reported_hr)

```

Remove awkward sleep times above 24 hours
```{r}

daily_report_subset <- subset(daily_report_subset, daily_report_subset$sleep_time_reported_hr <= 24.0)

```


## Split the dataframe into uEMA and EMA data frames
use TIME and BURST days study mode for separation
```{r}

time_df <- subset(daily_report_subset, daily_report_subset$study_mode == "TIME")
burst_df <- subset(daily_report_subset, daily_report_subset$study_mode == "BURST")

```

keep only watch assigned days and only days after the watch assignment took place
```{r}
time_df <- subset(time_df, time_df$watch_assigned == "True")
```

Only include watch dates after the training date

```{r}

time_df$date_stamp <- as.POSIXct(time_df$date, format = "%Y-%m-%d")

p_ids <- unique(time_df$participant_ID)


for (p_id in p_ids){
  # print(p_id)
  start_date <- watch_users_df$watch_training_day[watch_users_df$participant_id == p_id]
  # print(start_date)
  time_df <- time_df[!(time_df$participant_ID == p_id & time_df$date_stamp <= start_date), ]
  # print(nrow(time_df))
}

```

## Convert prompt counts to numeric
```{r}

time_df$uema_prompted_num <- as.numeric(time_df$uema_prompted_num)
time_df$uema_completed_num <- as.numeric(time_df$uema_completed_num)


```


## Use sleep time reported to get the expected number of uEMA and burst EMA prompts

Rubric to be used:
uEMA num prompts = (24.0 - sleep_time - 0.50)*4.0 --> convert to integer
burst EMA num prompts = (24.0 - sleep_time - 1.0)*1 --> convert to integet

Define the constants
```{r}

uEMA_PER_HOUR = 4.0
EMA_PER_HOUR = 1.0
uEMA_BUFFER_HOUR = 0.5
EMA_BUFFER_HOUR = 1.0

DAY_HOUR = 24.0

```

Compute expected prompts for burst EMA
```{r}


burst_df$burst_ema_expected_num <- as.integer((DAY_HOUR - burst_df$sleep_time_reported_hr - EMA_BUFFER_HOUR)*EMA_PER_HOUR)

```

Compute expected promtps for uEMA
```{r}

time_df$uema_expected_num <- as.integer((DAY_HOUR - time_df$sleep_time_reported_hr - uEMA_BUFFER_HOUR)*uEMA_PER_HOUR)

```

## Convert response rate columns to numeric
```{r}
burst_df$burst_ema_completion_rate <- as.numeric(burst_df$burst_ema_completion_rate)
burst_df$burst_ema_compliance_rate <- as.numeric(burst_df$burst_ema_compliance_rate)

time_df$uema_completion_rate <- as.numeric(time_df$uema_completion_rate)
time_df$uema_compliance_rate <- as.numeric(time_df$uema_compliance_rate)


time_df$uema_validation_perc <- as.numeric(time_df$uema_validation_perc)

time_df$uema_undo_num <- as.numeric(time_df$uema_undo_num)

time_df$uema_resp_time_mean <- as.numeric(time_df$uema_resp_time_mean)

burst_df$date_object <- as.POSIXct(burst_df$date, format = "%Y-%m-%d")
time_df$date_object <- as.POSIXct(time_df$date, format = "%Y-%m-%d")

```

Convert count columns to numeric:
```{r}

burst_df$burst_ema_expected_num <- as.numeric(burst_df$burst_ema_expected_num)
burst_df$burst_ema_original_prompted_num <- as.numeric(burst_df$burst_ema_original_prompted_num)
burst_df$burst_ema_completed_num <- as.numeric(burst_df$burst_ema_completed_num)

time_df$uema_expected_num <- as.numeric(time_df$uema_expected_num)
time_df$uema_prompted_num <- as.numeric(time_df$uema_prompted_num)
time_df$uema_completed_num <- as.numeric(time_df$uema_completed_num)

```

First, let's assign the day number to each participant based on the sequence. Do this for both time_df and burst_df
```{r}

time_df <- time_df %>% group_by(participant_ID) %>% mutate(dayno = row_number())
burst_df <- burst_df %>% group_by(participant_ID) %>% mutate(dayno = row_number())

```



if there are dates to be filtered because of technical malfunction, include that code here
```{r}
## Read the missing data file here
missing_notes_file <- read.csv("/Users/adityaponnada/Downloads/time_study_data/missing_data_notes.csv", sep = ",", header = TRUE)

missing_notes_file <- subset(missing_notes_file, missing_notes_file$ACTION == "EXCLUDE")


# replace empty columns with the same date as the other column

missing_notes_file$START_DATE <- ifelse(missing_notes_file$START_DATE == "", missing_notes_file$END_DATE, missing_notes_file$START_DATE)
missing_notes_file$END_DATE <- ifelse(missing_notes_file$END_DATE == "", missing_notes_file$START_DATE, missing_notes_file$END_DATE)

# Convert to date time objects
missing_notes_file$START_DATE <- as.POSIXct(missing_notes_file$START_DATE, format = "%Y-%m-%d")
missing_notes_file$END_DATE <- as.POSIXct(missing_notes_file$END_DATE, format = "%Y-%m-%d")

missing_notes_file$P_ID <- paste0(missing_notes_file$P_ID, "@timestudy_com")


```

Filter out these dates from the combined daily report file - first the common dates
```{r}

all_pid_row <- subset(missing_notes_file, missing_notes_file$P_ID == "ALL_PARTICIPANTS@timestudy_com")

global_start_date <- all_pid_row$START_DATE
global_end_date <- all_pid_row$END_DATE

burst_df <- burst_df[(burst_df$date_object <= global_start_date | burst_df$date_object >= global_end_date), ]


```

Filter out other phone exclusion dates for the burst_df
```{r}



filter_exclusion_dates <- function(report_df, missing_df, device){
  missing_df <- subset(missing_df, missing_df$DEVICE == device | missing_df$DEVICE == "BOTH")
  missing_df <- subset(missing_df, missing_df$P_ID != "ALL_PARTICIPANTS@timestudy_com")
  pid_list <- unique(missing_df$P_ID)
  for (pid in pid_list){
    # print(paste0("participant: ", pid))
    missing_pid_subset <- subset(missing_df, missing_df$P_ID == pid)
    # print(nrow(missing_pid_subset))
    for (i in 1:nrow(missing_pid_subset)){
      # print(paste0("i: ", i))
      start_date <- missing_pid_subset$START_DATE[i]
      end_date <- missing_pid_subset$END_DATE[i]
      # print(start_date)
      # print(end_date)
      # print(paste0("nrow before: ", nrow(report_df)))
      test_subset <- subset(report_df, report_df$participant_ID == pid)
      test_subset <- test_subset[(test_subset$date_object >= start_date & test_subset$date_object <= end_date), ]
      # print(paste0("test_df nrow: ", nrow(test_subset)))
      # print(paste0("row: ", test_subset$date_object))
      report_df <- dplyr::setdiff(report_df, test_subset)
      # report_df <- subset(report_df, !(report_df$participant_ID == pid & report_df$date_object >= start_date) | (report_df$participant_ID == pid & report_df$date_object <= end_date))
      # print(paste0("nrow after: ", nrow(report_df)))
    }
  }
  
  return(report_df)
}


```

Get burst and time df updated
```{r}
# original number of rows 6168

burst_df <- filter_exclusion_dates(burst_df, missing_notes_file, "PHONE")

# original number of rows 13415
time_df <- filter_exclusion_dates(time_df, missing_notes_file, "WATCH")
```

Also check by removing outliers
```{r}

remove_outliers_from_df <- function(df){
  outliers <- c("uniformlyharmfulbush@timestudy_com", "penpalsandbanklifting@timstudy_com")
  df <- subset(df, df$participant_ID %!in% outliers)
  return(df)
}

```

Get non-outlier dfs
```{r}
time_df <- remove_outliers_from_df(time_df)
burst_df <- remove_outliers_from_df(burst_df)


```

## Create a comprehensive completion rate for uEMA
```{r}

time_df$uema_prompted_num <- as.numeric(time_df$uema_prompted_num)
time_df$uema_completed_num <- as.numeric(time_df$uema_completed_num)
time_df$uema_cs_completed <- as.numeric(time_df$uema_cs_completed)
time_df$uema_partial_completed_num <- as.numeric(time_df$uema_partial_completed_num)
time_df$uema_trivia_completed <- as.numeric(time_df$uema_trivia_completed)

time_df$uema_all_completion_rate <- (time_df$uema_completed_num + time_df$uema_cs_completed + time_df$uema_trivia_completed)/time_df$uema_prompted_num

```


## Add value caps for response rates
```{r}

burst_df$burst_ema_completion_rate[burst_df$burst_ema_completion_rate >= 1.0] <- 1.0
burst_df$burst_ema_compliance_rate[burst_df$burst_ema_compliance_rate >= 1.0] <- 1.0
time_df$uema_completion_rate[time_df$uema_completion_rate >= 1.0] <- 1.0
time_df$uema_compliance_rate[time_df$uema_compliance_rate >= 1.0] <- 1.0


```

## Rename participant status df column names

```{r}

names(participant_status_df)[names(participant_status_df) == 'participant_id'] <- 'participant_ID'

```

## Add participant status to time and bust dfs

```{r}
time_df <- merge(x = time_df, y = participant_status_df[ , c("participant_ID", "participant_status")], by = "participant_ID", all.x=TRUE)

burst_df <- merge(x = burst_df, y = participant_status_df[ , c("participant_ID", "participant_status")], by = "participant_ID", all.x=TRUE)


```

Write a code to get the list of participants from time_df, whose participant status is 'completed' AND the maximum dayno value is 190. First group by participants to get the max day no, then filter by dayno less than 190. The final dataframe should return the participant ID and their maximum day_no value
```{r}


test_data_completed <- time_df %>%
  group_by(participant_ID) %>%
  summarise(max_dayno = max(dayno)) %>%
  filter(max_dayno >= 180 & participant_ID %in% time_df$participant_ID[time_df$participant_status == "Completed"])

```

180 (8-9 months)--> 125, 200 --> 114, 220 (10 months) --> 107 participants. 240 (11 months) --> 76, 260 --> 4

Same for burst_df

```{r}

test_data_completed_burst <- burst_df %>%
  group_by(participant_ID) %>%
  summarise(max_dayno = max(dayno)) %>%
  filter(max_dayno <= 80 & participant_ID %in% burst_df$participant_ID[burst_df$participant_status == "Completed"])

```

**NOTE** in uEMA, 29 participants did not survive after 10 months (i.2., 220 days). That left, ~107 participants who completed. In case of EMA, everyone survived past 12 months.

## Get the days distribution for time and burst df based on participant status

```{r}

time_status_df <- time_df[, c("participant_ID", "participant_status")]


time_status_df <- time_status_df %>% dplyr::count(participant_ID, participant_status)


burst_status_df <- burst_df[, c("participant_ID", "participant_status")]

burst_status_df <- burst_status_df %>% count(participant_ID, participant_status)


```

## Plot the participant status distribution

```{r}

boxplot(time_status_df$n ~ time_status_df$participant_status, main = "uEMA days vs status")

boxplot(burst_status_df$n ~ burst_status_df$participant_status, main = "EMA days vs status")

```

## Describe EMA compliance and completion rates by group

```{r}

describeBy(burst_df$burst_ema_compliance_rate, group = burst_df$participant_status, mat=TRUE, digits=4)
describeBy(burst_df$burst_ema_completion_rate, group = burst_df$participant_status, mat=TRUE, digits=4)

```

## Describe uEMA compliance and completion rates by group

```{r}

describeBy(time_df$uema_compliance_rate, group = time_df$participant_status, mat=TRUE, digits=4)
describeBy(time_df$uema_completion_rate, group = time_df$participant_status, mat=TRUE, digits=4)

```
## Plot the compliance and completion distribution



```{r}
boxplot(burst_df$burst_ema_compliance_rate ~ burst_df$participant_status, main = "EMA compliance")
boxplot(burst_df$burst_ema_completion_rate ~ burst_df$participant_status, main = "EMA completion")
boxplot(time_df$uema_compliance_rate ~ time_df$participant_status, main = "uEMA compliance")
boxplot(time_df$uema_completion_rate ~ time_df$participant_status, main = "uEMA completion")


```

## Prep data for models - subset columns

```{r}
burst_df$date_stamp <- as.POSIXct(burst_df$date, format = "%Y-%m-%d")

burst_subset_df <- burst_df[, c("participant_ID", "date", "study_mode", "date_stamp", "uema_completed_num", "uema_prompted_num", "burst_ema_completed_num", "burst_ema_original_prompted_num", "burst_ema_expected_num", "participant_status")]

time_subset_df <- time_df[, c("participant_ID", "date", "study_mode", "date_stamp", "uema_completed_num", "uema_prompted_num", "burst_ema_completed_num", "burst_ema_original_prompted_num", "uema_expected_num", "participant_status")]
```

## Now riw bind them into one
```{r}

colnames(burst_subset_df)[9] <- "expected_num"
colnames(time_subset_df)[9] <- "expected_num"

clean_time_burst_df <- rbind(burst_subset_df, time_subset_df)

```

## Do some grouping and ordering
```{r}
clean_time_burst_df <- arrange(clean_time_burst_df, participant_ID, date_stamp)

```

Finally, create a sum column and convert to numerics

```{r}


cols.num <- c("uema_completed_num", "uema_prompted_num", "burst_ema_completed_num", "burst_ema_original_prompted_num", "expected_num")
clean_time_burst_df[cols.num] <- sapply(clean_time_burst_df[cols.num],as.numeric)

```


Convert NAs to zero
```{r}

clean_time_burst_df[is.na(clean_time_burst_df)] <- 0

```

Add into single column
```{r}

clean_time_burst_df$prompted <- clean_time_burst_df$uema_prompted_num + clean_time_burst_df$burst_ema_original_prompted_num
clean_time_burst_df$completed <- clean_time_burst_df$uema_completed_num + clean_time_burst_df$burst_ema_completed_num

```

Prepare data
```{r}
names(clean_time_burst_df) <- c("P_ID", "DATE", "TYPE", "DATE_STAMP", "UEMA_COMPLETED", "UEMA_PROMPTED", "EMA_COMPLETED", "EMA_PROMPTED", "TOTAL_EXPECTED", "STATUS", "TOTAL_PROMPTED", "TOTAL_COMPLETED")

```


Add a column of failures for expected and delivered prompts - correct for incorrect expected number of prompts
```{r}

for (i in 1:nrow(clean_time_burst_df)){
  if (clean_time_burst_df$TOTAL_EXPECTED[i] < clean_time_burst_df$TOTAL_PROMPTED[i]){
    clean_time_burst_df$TOTAL_EXPECTED[i] = clean_time_burst_df$TOTAL_PROMPTED[i]
  }
}



clean_time_burst_df$EXPD_MISSED <- clean_time_burst_df$TOTAL_EXPECTED - clean_time_burst_df$TOTAL_COMPLETED
clean_time_burst_df$PMPD_MISSED <- clean_time_burst_df$TOTAL_PROMPTED - clean_time_burst_df$TOTAL_COMPLETED


```

Convert TYPE to numeric
```{r}

clean_time_burst_df$TYPE_NUM[clean_time_burst_df$TYPE == "BURST"] <- 0
clean_time_burst_df$TYPE_NUM[clean_time_burst_df$TYPE == "TIME"] <- 1

```

## clear the buggy status days
```{r}
clean_time_burst_df <- subset(clean_time_burst_df, clean_time_burst_df$STATUS != 0)

```

## completed participants model
```{r}

test_df <- subset(clean_time_burst_df, clean_time_burst_df$STATUS == "Completed")

compliance_mod <- glmer(cbind(TOTAL_COMPLETED, EXPD_MISSED) ~ TYPE_NUM + (1 | P_ID), family = "binomial", data=test_df)

summary(compliance_mod)

compliance_se <- sqrt(diag(vcov(compliance_mod)))
# table of estimates with 95% CI
(compiance_tab <- cbind(Est = fixef(compliance_mod), LL = fixef(compliance_mod) - 1.96 * compliance_se, UL = fixef(compliance_mod) + 1.96 *
    compliance_se))

exp(compiance_tab)

```



## Run the random intercept model for compliance uEMA vs EMA

```{r}

compliance_model <- function(df, status_type){
  subset_df <- subset(df, df$STATUS == status_type)
  mod <- glmer(cbind(TOTAL_COMPLETED, EXPD_MISSED) ~ TYPE_NUM + (1 | P_ID), family = "binomial", data=subset_df)
  print(summary(mod))
  
  se <- sqrt(diag(vcov(mod)))
# table of estimates with 95% CI
(tab <- cbind(Est = fixef(mod), LL = fixef(mod) - 1.96 * se, UL = fixef(mod) + 1.96 *
    se))

print(exp(tab))
  
}

```

## Completed participants compliance
```{r}
compliance_model(clean_time_burst_df, "Completed")
```

```{r}

compliance_model(clean_time_burst_df, "Withdrew")

```

```{r}

compliance_model(clean_time_burst_df, "Unenrolled")

```
## Run the random intercept model for completion uEMA vs EMA

```{r}

completion_model <- function(df, status_type){
  subset_df <- subset(df, df$STATUS == status_type)
  mod <- glmer(cbind(TOTAL_COMPLETED, PMPD_MISSED) ~ TYPE_NUM + (1 | P_ID), family = "binomial", data=subset_df)
  print(summary(mod))
  
  se <- sqrt(diag(vcov(mod)))
# table of estimates with 95% CI
(tab <- cbind(Est = fixef(mod), LL = fixef(mod) - 1.96 * se, UL = fixef(mod) + 1.96 *
    se))

print(exp(tab))
  
}

```

```{r}
completion_model(clean_time_burst_df, "Completed")
```

```{r}
completion_model(clean_time_burst_df, "Withdrew")
```

```{r}
completion_model(clean_time_burst_df, "Unenrolled")
```


## Create a plot friendlt dataset
```{r}

plot_df <- clean_time_burst_df[, c("TYPE", "TOTAL_PROMPTED", "TOTAL_COMPLETED", "TOTAL_EXPECTED", "STATUS")]

```

## Compute response rates
```{r}

plot_df$COMPLETION <- plot_df$TOTAL_COMPLETED/plot_df$TOTAL_PROMPTED
plot_df$COMPLIANCE <- plot_df$TOTAL_COMPLETED/plot_df$TOTAL_EXPECTED

```

Plot the response rare distribution ...
```{r out.width = '40%'}

plot_df <- plot_df[, c("TYPE", "STATUS", "COMPLIANCE", "COMPLETION")]

plot_df_long <- melt(plot_df, id.vars=c("TYPE","STATUS"))

plot_df_long <- subset(plot_df_long, plot_df_long$STATUS != '0')

plot_df_long$METHOD[plot_df_long$TYPE == 'BURST'] <- 'EMA'
plot_df_long$METHOD[plot_df_long$TYPE == 'TIME'] <- updated_string <- gsub(" ", "", paste('\U00B5','EMA'))

#then plot
p <- ggplot(plot_df_long, aes(variable, value,fill=TYPE)) + geom_violin() + facet_wrap(~STATUS)


```




```{r}

p <- ggplot(plot_df_long, aes(variable, value,fill=METHOD)) + geom_violin() + facet_wrap(~STATUS) +
  scale_fill_manual('Method', values = c('coral', 'cadetblue3')) +
  theme_bw() +
  xlab('') +
  ylab('Daily response rates for ...') +
  theme(text = element_text(size=15),
        axis.text.x = element_text(size=10), title = element_text(size=15), legend.position = "top", legend.justification.top = "left") +
  stat_summary(fun.data=mean_sdl, fun.args = list(mult = 1),
               geom="pointrange", color="black",
               shape = 18, size = 0.75,
               position = position_dodge(width = 0.9))

```


```{r}
p
```


## Add the number of days for each user in the time and burst dfs

```{r}
time_subset_df <- time_subset_df %>% group_by(participant_ID) %>% mutate(dayno = row_number())

```

```{r}
burst_subset_df <- burst_subset_df %>% group_by(participant_ID) %>% mutate(dayno = row_number())
```

## Add compliance and completion rates for plotting
```{r}

time_subset_df$completion_rate <- time_subset_df$uema_completed_num/time_subset_df$uema_prompted_num

time_subset_df$compliance_rate <- time_subset_df$uema_completed_num/time_subset_df$expected_num

```

```{r}

burst_subset_df$completion_rate <- burst_subset_df$burst_ema_completed_num/burst_subset_df$burst_ema_original_prompted_num

burst_subset_df$compliance_rate <- burst_subset_df$burst_ema_completed_num/burst_subset_df$expected_num


```

## Plot the seasonality plot for compliance and completion rate
basically a facet of participant status 3 columns, each plot EMA compliance and completion rates
```{r}


plot_seasonality_ema <- function(df, status_type){
  
  df <- subset(df, df$participant_status == status_type)
  
  to_keep <- c("dayno", "compliance_rate", "completion_rate")
  df <- df[, to_keep]
  
  df <- reshape2::melt(df, id.var='dayno')
  
  line_plot <- ggplot(data=df, aes(x=dayno, y=value, color = variable)) +
    # geom_line(size = 1) +
    # geom_point() +
    theme_bw() +
    scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.5)) +
    scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, by = 50)) +
    # scale_x_discrete(labels = c("Home", "School", "Work", "Friend", "Unlabeled", "Transit", "Other")) +
    # theme(axis.text.x = element_text(angle = 45, margin = margin(t = 5))) +
    # stat_summary(geom="ribbon", fun.data=mean_cl_normal, conf.int=0.95, fill="lightblue", alpha = 0.5) +
    # stat_summary(fun.y = mean, geom = "line", aes(ymax= ..y.., ymin = ..y..),
    #            width = 0.1, size = 1) +
    geom_smooth() +
    # scale_colour_manual("", values = c(Compliance = "blue", Completion = "red")) +
    # scale_y_continuous(breaks = c(0, 0.5, 1.0), label = c("0", "0.5", "1.0")) +
    labs(x = "Days in study", y = "Rate", color = "Rate type") +
    scale_color_manual(labels = c("Compliance rate", "Completion rate"), values = c("red", "blue")) +
    theme(axis.title = element_text(size = 15), axis.text.x = element_text(size = 15, colour = "black"), axis.text.y = element_text(size = 15, colour = "black"), title = element_text(size = 15), axis.title.x=element_blank(), legend.text = element_text(size = 15)) +
    ggtitle(status_type) +
    theme(
    legend.position = c(0.25, 0.15)
    # panel.grid.major.y = element_line(c(0, 25, 50, 75, 100),
    #   color = "#D9D9D9",
    #   size = 15)
  ) +
    guides(colour = guide_legend(nrow = 2))
  
  return(line_plot)
  
}

```


```{r}
plot_seasonality_uema <- function(df, status_type){
  
  df <- subset(df, df$participant_status == status_type)
  
  to_keep <- c("dayno", "compliance_rate", "completion_rate")
  df <- df[, to_keep]
  
  df <- reshape2::melt(df, id.var='dayno')
  
  line_plot <- ggplot(data=df, aes(x=dayno, y=value, color = variable)) +
    # geom_line(size = 1) +
    # geom_point() +
    theme_bw() +
    scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.5)) +
    scale_x_continuous(limits = c(0, 260), breaks = seq(0, 260, by = 130)) +
    # scale_x_discrete(labels = c("Home", "School", "Work", "Friend", "Unlabeled", "Transit", "Other")) +
    # theme(axis.text.x = element_text(angle = 45, margin = margin(t = 5))) +
    # stat_summary(geom="ribbon", fun.data=mean_cl_normal, conf.int=0.95, fill="lightblue", alpha = 0.5) +
    # stat_summary(fun.y = mean, geom = "line", aes(ymax= ..y.., ymin = ..y..),
    #            width = 0.1, size = 1) +
    geom_smooth() +
    # scale_colour_manual("", values = c(Compliance = "blue", Completion = "red")) +
    # scale_y_continuous(breaks = c(0, 0.5, 1.0), label = c("0", "0.5", "1.0")) +
    labs(x = "Days in study", y = "Rate", color = "Rate type") +
    scale_color_manual(labels = c("Compliance rate", "Completion rate"), values = c("red", "blue")) +
    theme(axis.title = element_text(size = 15), axis.text.x = element_text(size = 15, colour = "black"), axis.text.y = element_text(size = 15, colour = "black"), title = element_text(size = 15), axis.title.x=element_blank(), legend.text = element_text(size = 15)) +
    ggtitle(status_type) +
    theme(
    legend.position = c(0.25, 0.15)
    # panel.grid.major.y = element_line(c(0, 25, 50, 75, 100),
    #   color = "#D9D9D9",
    #   size = 15)
  ) +
    guides(colour = guide_legend(nrow = 2))
  
  return(line_plot)
  
}
```


## Plot to get number of participants per day
```{r}

plot_num_part_days <- function(df, type, status_type){
  
  if (type == "uema"){
    max_limit = 260
    day_type = "µEMA"
    
  } else if (type == "ema"){
    max_limit = 100
    day_type = "EMA"
  }
  
  split_val = max_limit/2
  
  df <- subset(df, df$participant_status == status_type)
  
  
  keep_names <- c("participant_ID", "dayno")
  df <- df[, keep_names]
  
  # df <- df %>% group_by(participant_ID) %>% mutate(actual_days = row_number())
  # 
  # 
  # df <- df[, c("participant_ID", "actual_days")]
  
  
  # agg_df <- distinct(df)
  
  agg_df <- aggregate(df$dayno, by = list(df$dayno), FUN = length)
  names(agg_df) <- c("Days", "Num_Ps")
  
  agg_df$Days <- as.numeric(agg_df$Days)
  
  # agg_df <- summarise(group_by(df,Participant_ID, EXPOSURE_DAY_NO),length(Participant_ID))
  # names(agg_df) <- c("Participant_ID", "max_expo_day", "COUNT")
  # 
  # agg_df <- agg_df %>%
  # group_by(Participant_ID, max_expo_day) %>%
  # mutate(COMPLETION_RATE = COUNT / sum(COUNT))
  # 
  # agg_df <- subset(agg_df, agg_df$ANSWER_STATUS == "Answered")
  # 
  # agg_df$max_expo_day <- as.numeric(agg_df$max_expo_day)
  # 
  line_plot <- ggplot(data=agg_df, aes(x=Days, y=Num_Ps)) +
    geom_line(size = 1) +
    # geom_smooth(aes(x=Days, y=Num_Ps), color='black') + 
    # geom_point() +
    theme_bw() +
    scale_y_continuous(limits = c(0, 150), breaks = seq(0, 150, by = 50)) +
    scale_x_continuous(limits = c(0, max_limit), breaks = seq(0, max_limit, by = split_val)) +
    # scale_x_discrete(labels = c("Home", "School", "Work", "Friend", "Unlabeled", "Transit", "Other")) +
    # theme(axis.text.x = element_text(angle = 45, margin = margin(t = 5))) +
    # stat_summary(geom="ribbon", fun.data=mean_cl_normal, conf.int=0.95, fill="lightblue", alpha = 0.5) +
    # stat_summary(fun.y = mean, geom = "line", aes(ymax= ..y.., ymin = ..y..),
    #            width = 0.1, size = 1) +
    # scale_y_continuous(breaks = c(0, 0.5, 1.0), label = c("0", "0.5", "1.0")) +
    labs(x = paste0(day_type, " days"), y = "No. participants") +
    theme(axis.title = element_text(size = 15), axis.text.x = element_text(size = 15, colour = "black"), axis.text.y = element_text(size = 15, colour = "black"), title = element_text(size = 15)) 
  # + ggtitle(paste0(day_type, " ", status_type))
   
  
   # ylim(0, 1) +
    # xlim(0, 300)
  
  # box_plot <- ggplot(agg_df, aes(x=DAYS_IN_THE_STUDY, y=COMPLETION_RATE)) + 
  # geom_boxplot() +
  #   ggtitle("Completion | Days in the study")
  # 
  # summary_object <- describeBy(agg_df$COMPLETION_RATE, group = agg_df$DAYS_IN_THE_STUDY)
  # 
  # print(summary_object)
  
  # return_list <- c(summary_object, box_plot)
  
  return(line_plot)
}

```

## Put the plots together
```{r}

library(ggpubr)

uema_com_plot <- plot_seasonality_uema(time_subset_df, "Completed")
uema_wdr_plot <- plot_seasonality_uema(time_subset_df, "Withdrew")
uema_unen_plot <- plot_seasonality_uema(time_subset_df, "Unenrolled")

ema_com_plot <- plot_seasonality_ema(burst_subset_df, "Completed")
ema_wdr_plot <- plot_seasonality_ema(burst_subset_df, "Withdrew")
ema_unen_plot <- plot_seasonality_ema(burst_subset_df, "Unenrolled")

uema_num_com <- plot_num_part_days(time_subset_df, "uema", "Completed")
uema_num_wdr <- plot_num_part_days(time_subset_df, "uema", "Withdrew")
uema_num_unen <- plot_num_part_days(time_subset_df, "uema", "Unenrolled")

ema_num_com <- plot_num_part_days(burst_subset_df, "ema", "Completed")
ema_num_wdr <- plot_num_part_days(burst_subset_df, "ema", "Withdrew")
ema_num_unen <- plot_num_part_days(burst_subset_df, "ema", "Unenrolled")


uema_arranged <- ggarrange(uema_com_plot, uema_wdr_plot, uema_unen_plot, uema_num_com, uema_num_wdr, uema_num_unen, ncol = 3, nrow = 2)

ema_arranged <- ggarrange(ema_com_plot, ema_wdr_plot, ema_unen_plot, ema_num_com, ema_num_wdr, ema_num_unen, ncol = 3, nrow = 2)

```
```{r}

uema_arranged

```

```{r}

ema_arranged

```


## Model with interaction effect (Completion rate)
```{r}

completion_model_full <- function(df){
  # subset_df <- subset(df, df$STATUS == status_type)
  subset_df = df
  mod <- glmer(cbind(TOTAL_COMPLETED, PMPD_MISSED) ~ TYPE_NUM + TYPE_NUM*STATUS + (1 | P_ID), family = "binomial", data=subset_df, control = glmerControl(optimizer ="Nelder_Mead"))
  print(summary(mod))
  
  se <- sqrt(diag(vcov(mod)))
# table of estimates with 95% CI
(tab <- cbind(Est = fixef(mod), LL = fixef(mod) - 1.96 * se, UL = fixef(mod) + 1.96 *
    se))

print(exp(tab))
  
}

```

Testing the model (IGNORE)
```{r}
completion_model_full(clean_time_burst_df)

```

## Model with interaction effect (Compliance rate)
```{r}

compliance_model_full <- function(df){
  # subset_df <- subset(df, df$STATUS == status_type)
  subset_df = df
  mod <- glmer(cbind(TOTAL_COMPLETED, EXPD_MISSED) ~ TYPE_NUM + TYPE_NUM*STATUS + (1 | P_ID), family = "binomial", data=subset_df, control = glmerControl(optimizer ="Nelder_Mead"))
  print(summary(mod))
  
  se <- sqrt(diag(vcov(mod)))
# table of estimates with 95% CI
(tab <- cbind(Est = fixef(mod), LL = fixef(mod) - 1.96 * se, UL = fixef(mod) + 1.96 *
    se))

print(exp(tab))
  
}

```

```{r}
compliance_model_full(clean_time_burst_df)

```


### Get status count per participant in the final dataset
```{r}

per_participant_df <- clean_time_burst_df %>%
  group_by(P_ID) %>%
  filter(row_number()==1)

```

```{r}

table(per_participant_df$STATUS)

```


## Summary compliance and completion rate functions

### First, for overall EMA types
```{r}

## Compliance rate

sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'BURST', ]$TOTAL_COMPLETED)/sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'BURST', ]$TOTAL_EXPECTED)

```

```{r}

## Completion rate

sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'BURST', ]$TOTAL_COMPLETED)/sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'BURST', ]$TOTAL_PROMPTED)

```

```{r}

## Compliance rate

sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'TIME', ]$TOTAL_COMPLETED)/sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'TIME', ]$TOTAL_EXPECTED)

```

```{r}

## Completion rate

sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'TIME', ]$TOTAL_COMPLETED)/sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'TIME', ]$TOTAL_PROMPTED)

```

## Overall rates by group for uEMA
```{r}

## Completion rates

sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'TIME' & clean_time_burst_df$STATUS == 'Completed', ]$TOTAL_COMPLETED)/sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'TIME' & clean_time_burst_df$STATUS == 'Completed', ]$TOTAL_PROMPTED)

sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'TIME' & clean_time_burst_df$STATUS == 'Withdrew', ]$TOTAL_COMPLETED)/sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'TIME' & clean_time_burst_df$STATUS == 'Withdrew', ]$TOTAL_PROMPTED)

sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'TIME' & clean_time_burst_df$STATUS == 'Unenrolled', ]$TOTAL_COMPLETED)/sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'TIME' & clean_time_burst_df$STATUS == 'Unenrolled', ]$TOTAL_PROMPTED)

## Compliance rates

sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'TIME' & clean_time_burst_df$STATUS == 'Completed', ]$TOTAL_COMPLETED)/sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'TIME' & clean_time_burst_df$STATUS == 'Completed', ]$TOTAL_EXPECTED)

sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'TIME' & clean_time_burst_df$STATUS == 'Withdrew', ]$TOTAL_COMPLETED)/sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'TIME' & clean_time_burst_df$STATUS == 'Withdrew', ]$TOTAL_EXPECTED)

sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'TIME' & clean_time_burst_df$STATUS == 'Unenrolled', ]$TOTAL_COMPLETED)/sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'TIME' & clean_time_burst_df$STATUS == 'Unenrolled', ]$TOTAL_EXPECTED)

```

```{r}

## Completion rates

sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'BURST' & clean_time_burst_df$STATUS == 'Completed', ]$TOTAL_COMPLETED)/sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'BURST' & clean_time_burst_df$STATUS == 'Completed', ]$TOTAL_PROMPTED)

sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'BURST' & clean_time_burst_df$STATUS == 'Withdrew', ]$TOTAL_COMPLETED)/sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'BURST' & clean_time_burst_df$STATUS == 'Withdrew', ]$TOTAL_PROMPTED)

sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'BURST' & clean_time_burst_df$STATUS == 'Unenrolled', ]$TOTAL_COMPLETED)/sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'BURST' & clean_time_burst_df$STATUS == 'Unenrolled', ]$TOTAL_PROMPTED)

## Compliance rates

sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'BURST' & clean_time_burst_df$STATUS == 'Completed', ]$TOTAL_COMPLETED)/sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'BURST' & clean_time_burst_df$STATUS == 'Completed', ]$TOTAL_EXPECTED)

sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'BURST' & clean_time_burst_df$STATUS == 'Withdrew', ]$TOTAL_COMPLETED)/sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'BURST' & clean_time_burst_df$STATUS == 'Withdrew', ]$TOTAL_EXPECTED)

sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'BURST' & clean_time_burst_df$STATUS == 'Unenrolled', ]$TOTAL_COMPLETED)/sum(clean_time_burst_df[clean_time_burst_df$TYPE == 'BURST' & clean_time_burst_df$STATUS == 'Unenrolled', ]$TOTAL_EXPECTED)

```
## Compliance and completion summary at the participant level

## Create participant level data frames
This data frame is to get a wide form for each participant

First, we start with the time_df for uema

```{r}

time_keep_cols <- c("participant_ID", "uema_completed_num", "uema_prompted_num", "uema_expected_num", "uema_validation_perc")

selected_TIME_df <- time_df[, time_keep_cols]

```

Now create a function to return the completely aggregated df
```{r}

aggregate_time_df <- function(df){
  
  df1 <- df[, c("participant_ID", "uema_completed_num", "uema_prompted_num", "uema_expected_num")]
  num_time_days_df <- df %>% dplyr::count(participant_ID)
  df2 <- aggregate(.~participant_ID, df1, sum)
  df3 <- aggregate(uema_validation_perc~participant_ID, df, mean, na.rm=TRUE, na.action=na.pass)
  df2$num_time_days <- num_time_days_df$n
  df2 <- join(df2, df3)
  return(df2)
  
}

```

Use the function to get the aggregate df

```{r}

time_pid_df <- aggregate_time_df(selected_TIME_df)

```

Add compliance and completion rate columns

```{r}

time_pid_df$uema_completion_rate <- time_pid_df$uema_completed_num/time_pid_df$uema_prompted_num
time_pid_df$uema_compliance_rate <- time_pid_df$uema_completed_num/time_pid_df$uema_expected_num

```

Second, we do the same with burst EMA
```{r}

burst_keep_cols <- c("participant_ID", "burst_ema_completed_num", "burst_ema_original_prompted_num", "burst_ema_expected_num")

selected_BURST_df <- burst_df[, burst_keep_cols]

```

Now create a function to return the completely aggregated df
```{r}

selected_BURST_df$burst_ema_completed_num <- as.numeric(selected_BURST_df$burst_ema_completed_num)
selected_BURST_df$burst_ema_original_prompted_num <- as.numeric(selected_BURST_df$burst_ema_original_prompted_num)
selected_BURST_df$burst_ema_expected_num <- as.numeric(selected_BURST_df$burst_ema_expected_num)

aggregate_burst_df <- function(df){
  
  df1 <- df[, c("participant_ID", "burst_ema_completed_num", "burst_ema_original_prompted_num", "burst_ema_expected_num")]
  num_burst_days_df <- df %>% dplyr::count(participant_ID)
  df2 <- aggregate(.~participant_ID, df1, sum)
  df2$num_burst_days <- num_burst_days_df$n
  return(df2)
  
}

```

Use the function to get the aggregate df

```{r}

burst_pid_df <- aggregate_burst_df(selected_BURST_df)

```

Add compliance and completion rate columns
```{r}

burst_pid_df$burst_completion_rate <- burst_pid_df$burst_ema_completed_num/burst_pid_df$burst_ema_original_prompted_num
burst_pid_df$burst_compliance_rate <- burst_pid_df$burst_ema_completed_num/burst_pid_df$burst_ema_expected_num

```

## Join with participant status
```{r}

time_pid_df <- merge(time_pid_df, participant_status_df, by = 'participant_ID')
burst_pid_df <- merge(burst_pid_df, participant_status_df, by = 'participant_ID')

```


## Get average compliance and completion rates at the participant level
```{r}
describeBy(time_pid_df$uema_completion_rate, group = time_pid_df$participant_status, mat=TRUE, digits=4)
describeBy(time_pid_df$uema_compliance_rate, group = time_pid_df$participant_status, mat=TRUE, digits=4)

```

```{r}
describeBy(burst_pid_df$burst_completion_rate, group = burst_pid_df$participant_status, mat=TRUE, digits=4)
describeBy(burst_pid_df$burst_compliance_rate, group = burst_pid_df$participant_status, mat=TRUE, digits=4)
```



## Write the status type vs IDs to a file
```{r}
df_to_write = per_participant_df[, c('P_ID', 'STATUS')]
write.csv(df_to_write, "/Users/adityaponnada/Downloads/participant_6m_status.csv")

```

## Add covariates to compliance and completion models
Next, we will test the model by adding demographic variables as covariates to compliance and completion models
```{r}

## First, we will add the demographic variables to the participant level data frames
demo_df <- read.csv("/Users/adityaponnada/Downloads/time_study_data/demo_data_v1.csv")

## Only keep age and gender columns
demo_df <- demo_df[, c('visualizerid', 'age_years_a5db34', 'sexatbirth_eedb91')]

## Rename columns to be more readable
colnames(demo_df) <- c('P_ID', 'Age', 'Sex')

## Add @timestudy_com to Participant_ID for each row
demo_df$P_ID <- paste0(demo_df$P_ID, '@timestudy_com')

## Keep only those participants who have been used in the analysis
demo_df <- subset(demo_df, demo_df$P_ID %in% unique(clean_time_burst_df$P_ID))

```

Next, we combine the clean_time_burst_df with the demo_df at the participant level. But we only keep the age and sex columns from demo_df
```{r}

time_pid_demo_df <- merge(clean_time_burst_df, demo_df, by = 'P_ID')

```

## Run the logistic regression model by adding age and sex
First, we will run it for the compliance model as above
```{r}

compliance_model_demo_full <- function(df){
  # subset_df <- subset(df, df$STATUS == status_type)
  subset_df = df
  mod <- glmer(cbind(TOTAL_COMPLETED, EXPD_MISSED) ~ TYPE_NUM + TYPE_NUM*STATUS + Age + Sex + (1 | P_ID), family = "binomial", data=subset_df, control = glmerControl(optimizer ="Nelder_Mead"))
  print(summary(mod))
  
  se <- sqrt(diag(vcov(mod)))
# table of estimates with 95% CI
(tab <- cbind(Est = fixef(mod), LL = fixef(mod) - 1.96 * se, UL = fixef(mod) + 1.96 *
    se))

print(exp(tab))
  
}

```

Now test the model
```{r}

compliance_model_demo_full(time_pid_demo_df)

```
Now we do the same thing for completion model
```{r}

completion_model_demo_full <- function(df){
  # subset_df <- subset(df, df$STATUS == status_type)
  subset_df = df
  mod <- glmer(cbind(TOTAL_COMPLETED, PMPD_MISSED) ~ TYPE_NUM + TYPE_NUM*STATUS + Age + Sex + (1 | P_ID), family = "binomial", data=subset_df, control = glmerControl(optimizer ="Nelder_Mead"))
  print(summary(mod))
  
  se <- sqrt(diag(vcov(mod)))
# table of estimates with 95% CI
(tab <- cbind(Est = fixef(mod), LL = fixef(mod) - 1.96 * se, UL = fixef(mod) + 1.96 *
    se))

print(exp(tab))
  
}

```

Now we test this model
```{r}

completion_model_demo_full(time_pid_demo_df)

```
## Summarize uema validation perc
We use time_df for this analysis
```{r}

describeBy(time_df$uema_validation_perc, group = time_df$participant_status, mat=TRUE, digits=4)

```
```{r}
describe(time_df$uema_validation_perc)

mean(time_df$uema_validation_perc, na.rm=TRUE)
sd(time_df$uema_validation_perc, na.rm=TRUE)

```

