---
title: "uema_ema_corr"
output: html_document
date: "2025-01-16"
---

## Import library
```{r}

library(dplyr)
library(reshape2)
library(ggplot2)
library(psych)
library(readr)
library(purrr)
library(tidyr)
library(ggrepel)
library(cowplot)
library(GGally)
```

## Read EMA data
```{r}

ema_df <- read.csv("/Users/adityaponnada/Downloads/time_study_data/EMA_data.csv", sep = ",", header = TRUE)

```

## Read uEMA data
```{r}
# Set the path to folder
folder_path <- "/Users/adityaponnada/Downloads/time_study_data/uema_data"

# List all files matching the pattern B_*.csv
files <- list.files(path = folder_path, pattern = "watch_promptresponse_.*@timestudy_com\\.csv$", full.names = TRUE)

# Read and combine all CSV files
uema_df <- files %>%
  map_df(read_csv)


```

## Subset data frames
```{r}

keep_uema <- c("Participant_ID", "Question_X_ID", "Answer_Status", "Question_X_Text", "Question_X_Answer_Text")

uema_df <- uema_df[, keep_uema]

```

### Check distributions
```{r}

table(uema_df$Answer_Status)

table(uema_df$Question_X_ID)

```

### Check participant distribution
```{r}

n_distinct(uema_df$Participant_ID)

```

## Keep only completed responses
```{r}

uema_df <- subset(uema_df, Answer_Status %in% c("Completed", "CompletedThenDismissed", "PartiallyCompleted"))

```

### Reformat question ID
```{r}

uema_df$Question_X_ID <- sub("_.*", "", uema_df$Question_X_ID)


```

### Keep only relevant questions
```{r}

uema_questions <- c("tense", "stress", "sad", "routine", "relax", "nervous", "happy", "frust", "focus", "fatigue", "control")

uema_df <- subset(uema_df, Question_X_ID %in% uema_questions)

```

### Score responses
```{r}

uema_df <- uema_df %>%
  mutate(Answer_Score = case_when(
    Question_X_Answer_Text == "Yes" ~ 3,
    Question_X_Answer_Text == "Sort of" ~ 2,
    Question_X_Answer_Text == "No" ~ 1,
    TRUE ~ NA_real_  # This handles any other values not specified above
  ))

```

### Remove remaining NOT_ANS
```{r}

uema_df <- subset(uema_df, !is.na(uema_df$Answer_Score))

```


### Compute variance for each question
```{r}

uema_wide_df <- uema_df %>%
  group_by(Participant_ID, Question_X_ID) %>%
  summarise(Answer_Score_Var = var(Answer_Score, na.rm = TRUE)) %>%
  pivot_wider(names_from = Question_X_ID, values_from = Answer_Score_Var)

```

## EMA data prep - filter the relevant columns
```{r}

ema_df <- subset(ema_df, ema_df$Answer_Status %in% c("Completed", "PartiallyCompleted"))

```

### keep only selected columns
```{r}

keep_ema <- c("participant_id", "Answer_Status", "x01_sad", "x02_happy", "x03_fatigued", "x05_relaxed", "x06_tense", "x07_stressed"  , "x08_frustrated", "x09_nervous", "x10_focused", "x11_control", "x14_routine")

ema_df <- ema_df[, keep_ema]

```

### Rename columns
```{r}

colnames(ema_df) <- c("Participant_ID", "Answer_Status", "sad", "happy", "fatigue", "relax", "tense", "stress", "frust", "nervous", "focus", "control", "routine")

```

### Compute variance for each question
```{r}

ema_wide_df <- ema_df %>%
  group_by(Participant_ID) %>%
  summarise(across(c(sad, happy, fatigue, relax, tense, stress, frust, nervous, focus, control, routine), var, na.rm = TRUE))

```

## Plot uema and ema data in grids
```{r}

uema_plot_df <- uema_wide_df %>% 
  pivot_longer(cols = -Participant_ID, names_to = "variable", values_to = "value")

uema_var_plot <- ggplot(uema_plot_df, aes(x = value)) +
  geom_histogram(bins = 30, fill = "steelblue", color = "white") +
  facet_wrap(~ variable, scales = "free", ncol = 4) +
  theme_minimal() +
  xlim(0, 4) +
  labs(title = "Histograms of All uEMA construct variances",
       x = "Value",
       y = "Count")

```
### For EMA
```{r}



ema_plot_df <- ema_wide_df %>% 
  pivot_longer(cols = -Participant_ID, names_to = "variable", values_to = "value")

ema_var_plot <- ggplot(ema_plot_df, aes(x = value)) +
  geom_histogram(bins = 30, fill = "steelblue", color = "white") +
  facet_wrap(~ variable, scales = "free", ncol = 4) +
  theme_minimal() +
  xlim(0,4) +
  labs(title = "Histograms of All EMA construct variances",
       x = "Value",
       y = "Count")

```

## EMA score mapped to uEMA
First, get the list of columns
```{r}
ema_col_list <- c("sad", "happy", "fatigue", "relax", "tense", "stress", "frust", "nervous", "focus", "control", "routine")
```

Then apply the function

```{r}

ema_3p_df <- ema_df %>%
  mutate(across(ema_col_list, 
                ~ case_when(
                  . %in% c(4, 5) ~ 3,
                  . %in% c(2, 3) ~ 2,
                  . == 1 ~ 1,
                  TRUE ~ NA_real_
                )))

```

### Compute variance for each question
```{r}

ema_3p_wide_df <- ema_3p_df %>%
  group_by(Participant_ID) %>%
  summarise(across(c(sad, happy, fatigue, relax, tense, stress, frust, nervous, focus, control, routine), var, na.rm = TRUE))

```

### Plot ema 3p variance distribution
```{r}

ema_3p_plot_df <- ema_3p_wide_df %>% 
  pivot_longer(cols = -Participant_ID, names_to = "variable", values_to = "value")

ema_3p_var_plot <- ggplot(ema_3p_plot_df, aes(x = value)) +
  geom_histogram(bins = 30, fill = "steelblue", color = "white") +
  facet_wrap(~ variable, scales = "free", ncol = 4) +
  theme_minimal() +
  xlim(0,4) +
  labs(title = "Histograms of All EMA construct variances (3 point)",
       x = "Value",
       y = "Count")

```

## Rename columns for uEMA and EMA
We will rename each of the column name except for participant_ID to have a prefix of either uema_ or ema_
```{r}

column_rename <- function(df, prefix) {
  colnames(df)[-1] <- paste0(prefix, "_", colnames(df)[-1])
  return(df)
}

```

Now we apply the function
```{r}

uema_wide_df <- column_rename(uema_wide_df, "uema")

```

Now apply to EMA data
```{r}


ema_3p_wide_df <- column_rename(ema_3p_wide_df, "ema")

```

## Read the participant status data
```{r}

participant_status_dat_df <- read.csv("/Users/adityaponnada/Downloads/time_study_data/participant_status_tracking_v2.csv", sep = ",", header = TRUE)

participant_status_dat_df$Participant_ID <- paste0(participant_status_dat_df$Visualizer.ID, "@timestudy_com")

```

Get the daily report participant list from daily_report_subset
```{r}

final_participant_list <- unique(daily_report_subset$participant_ID)

```

### Filter the participant status data
```{r}

participant_status_dat_df <- subset(participant_status_dat_df, participant_status_dat_df$Participant_ID %in% final_participant_list)

```

### Only keep the Participant ID and the Participant Status column in the data frame
```{r}

participant_status_dat_df <- participant_status_dat_df[, c("Participant_ID", "Participant.Status")]

```

First, add @timestudy_com to participant ID in ema_3p_wide_df
```{r}
ema_3p_wide_df$Participant_ID <- paste0(ema_3p_wide_df$Participant_ID, "@timestudy_com")
```


### Filter uEMA and EMA data based on final participant list
```{r}

uema_wide_df <- subset(uema_wide_df, uema_wide_df$Participant_ID %in% final_participant_list)

ema_3p_wide_df <- subset(ema_3p_wide_df, ema_3p_wide_df$Participant_ID %in% final_participant_list)

```

### Find out the users who are in uEMA but not in ema data
```{r}

uema_not_in_ema <- setdiff(uema_wide_df$Participant_ID, ema_3p_wide_df$Participant_ID)

```

### Merge uEMA and EMA data by Participant ID.
But we will only keep the common participant_IDs in uema and EMA
```{r}

combined_df <- merge(uema_wide_df, ema_3p_wide_df, by = "Participant_ID")

```

Next, we also add the participant status column to this dataframe. We also ensure that the new column is the second column
```{r}

combined_df1 <- merge(combined_df, participant_status_dat_df, by = "Participant_ID")


```

### Next we compute the pearson correlation between uEMA and EMA data for each construct
We then save it in a dataframe with the construct name and the correlation value and p-value
```{r}

correlation_df <- data.frame()
correr <- function(df, construct) {
  cor_val <- cor.test(df[, c(paste0("uema_", construct))], df[, c(paste0("ema_", construct))], method="pearson")
  return(c(cor_val$estimate, cor_val$p.value))
}

```

Test the correlation for all the constructs and print them one by one.
THIS IS AN IMPORTANT TABLE TO REPORT
```{r}

for (construct in c("sad", "happy", "fatigue", "relax", "tense", "stress", "frust", "nervous", "focus", "control", "routine")) {
  cor_val <- correr(combined_df1, construct)
  correlation_df <- rbind(correlation_df, data.frame(construct = construct, correlation = cor_val[[1]], p_value = cor_val[[2]]))
}

```

## Plot individual construct correlations
Here, we will plot each constructs scatterplots with the correlation value and p-value displayed on the plot.
```{r}

correlation_plot <- ggplot(correlation_df, aes(x = correlation, y = p_value, label = construct)) +
  geom_point() +
  geom_text_repel() +
  labs(title = "Correlation between uEMA and EMA constructs",
       x = "Correlation",
       y = "P-value")

```

Create a function to rename constructs. This function will take the construct names such as sad, happy, fatigue, etc. and return the full construct names such as "Sadness", "Happiness", "Fatigue", etc.
```{r}

rename_construct <- function(construct) {
  construct_names <- c("sad" = "Sadness",
                       "happy" = "Happiness",
                       "fatigue" = "Fatigue",
                       "relax" = "Relaxation",
                       "tense" = "Tension",
                       "stress" = "Stress",
                       "frust" = "Frustration",
                       "nervous" = "Nervousness",
                       "focus" = "Focus",
                       "control" = "Control",
                       "routine" = "Routine")
  return(construct_names[[construct]])
}

```


In the next plot, we will use the combined_df1 dataframe to plot the scatterplots for each construct. For example, we will plot the scatterplot for sad construct where the x-axis is the uema_sad and the y-axis is the ema_sad. We will also display the correlation value and p-value on the plot.
```{r}

construct_plot <- function(df, construct) {
  construct_name <- rename_construct(construct)
  plot_df <- df %>% select(paste0("uema_", construct), paste0("ema_", construct))
  plot_df <- plot_df[complete.cases(plot_df), ]
  cor_val <- cor.test(plot_df[,1], plot_df[,2], method="pearson")
  plot <- ggplot(plot_df, aes(x = plot_df[,1], y = plot_df[,2])) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE) +
    # geom_text(x = 1, y = 1, label = paste("Correlation:", round(cor_val$estimate, 2), "P-value:", round(cor_val$p.value, 2))) +
    labs(title = paste0(construct_name, " (r=", round(cor_val$estimate, 2), ")"),
         x = paste0("\u03BC", "EMA Variance"),
         y = "EMA Variance") +
    xlim(0, 1) +
    ylim(0, 1) +
    theme_bw() +
    theme(panel.background = element_rect(fill = "white"))
  return(plot)
}

```


Next, we will create a grid of all the 11 constructs and plot them side by side. We will create a grid of 3x4 plots.
```{r}

construct_plots <- list()
for (construct in c("sad", "happy", "fatigue", "relax", "tense", "stress", "frust", "nervous", "focus", "control", "routine")) {
  construct_plots[[construct]] <- construct_plot(combined_df1, construct)
}

```

Now we will arrange them in a 3X4 grid
```{r}

construct_plots_grid <- plot_grid(plotlist = construct_plots, ncol = 4, nrow = 3, rel_heights = c(1, 1, 1))


```

## Split the data into two groups based on the participant status
```{r}

completed_participants <- subset(combined_df1, combined_df1$Participant.Status == "Completed")
withdrawn_participants <- subset(combined_df1, combined_df1$Participant.Status == "Withdrew")
unenrolled_participants <- subset(combined_df1, combined_df1$Participant.Status == "Unenrolled")

```

### Compute correlation for each group across uEMA and EMA constructs
first for completed participants
```{r}

correlation_df_completed <- data.frame()
for (construct in c("sad", "happy", "fatigue", "relax", "tense", "stress", "frust", "nervous", "focus", "control", "routine")) {
  cor_val <- correr(completed_participants, construct)
  correlation_df_completed <- rbind(correlation_df_completed, data.frame(construct = construct, correlation = cor_val[[1]], p_value = cor_val[[2]]))
}

```

Then, for unenrolled participants
```{r}

correlation_df_unenrolled <- data.frame()
for (construct in c("sad", "happy", "fatigue", "relax", "tense", "stress", "frust", "nervous", "focus", "control", "routine")) {
  cor_val <- correr(unenrolled_participants, construct)
  correlation_df_unenrolled <- rbind(correlation_df_unenrolled, data.frame(construct = construct, correlation = cor_val[[1]], p_value = cor_val[[2]]))
}

```

Finally, for withdrew participants
```{r}

correlation_df_withdrew <- data.frame()
for (construct in c("sad", "happy", "fatigue", "relax", "tense", "stress", "frust", "nervous", "focus", "control", "routine")) {
  cor_val <- correr(withdrawn_participants, construct)
  correlation_df_withdrew <- rbind(correlation_df_withdrew, data.frame(construct = construct, correlation = cor_val[[1]], p_value = cor_val[[2]]))
}

```

## Create a correlation matrix plot for all uEMA and EMA constructs
For this, we will use combined_df1 dataframe and plot the correlation matrix for all the constructs. Then we will create a heatmap of the correlation matrix.
```{r}


# Create the correlation plot
corr_matrix <- cor(combined_df[, -1], use = "complete.obs", method = "pearson")  # Exclude the ID column

# Melt the correlation matrix
melted_corr <- melt(corr_matrix)

# Create the heatmap
corr_plot_pairwise <- ggplot(data = melted_corr, aes(x = Var1, y = Var2, fill = value)) +
  geom_tile() +
  scale_fill_gradient2(low = "blue", high = "red", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Pearson\nCorrelation") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)) +
  coord_fixed() +
  labs(x = "", y = "") +
  geom_text(aes(label = round(value, 2)), size = 2)

```

## Get correlations and scatter plots for EMA with the original 5p scale as in ema_wide_df
First, we will rename the ema_wide_df columns to have a prefix of ema_5p
```{r}

ema_wide_df <- column_rename(ema_wide_df, "ema")

```

Next, we will add @timestudy_com to the participant ID in ema_wide_df
```{r}

ema_wide_df$Participant_ID <- paste0(ema_wide_df$Participant_ID, "@timestudy_com")

```


Next, we will merge ema_wide and uema_wide dataframes by Participant ID
```{r}

combined_df2 <- merge(uema_wide_df, ema_wide_df, by = "Participant_ID")

```

Next, we will compute the correlation between uEMA and EMA data for each construct. We will do this by conducting a correlation test using pearson correlation for each construct
```{r}

correlation_df_5p <- data.frame()
for (construct in c("sad", "happy", "fatigue", "relax", "tense", "stress", "frust", "nervous", "focus", "control", "routine")) {
  cor_val <- correr(combined_df2, construct)
  correlation_df_5p <- rbind(correlation_df_5p, data.frame(construct = construct, correlation = cor_val[[1]], p_value = cor_val[[2]]))
}

```


### Color code participants in construct_plot based on Participant_ID
We will create a new construct_plot called construct_plot_coded where each point in the scatterplot will be color-coded based on the Participant_ID. We will not add the legend for color codes.
```{r}


construct_plot_coded_list <- list()
construct_plot_coded <- function(df, construct) {
  plot_df <- df %>% select(paste0("uema_", construct), paste0("ema_", construct), Participant_ID)
  plot_df <- plot_df[complete.cases(plot_df), ]
  cor_val <- cor.test(plot_df[,1], plot_df[,2], method="pearson")
  plot <- ggplot(plot_df, aes(x = plot_df[,1], y = plot_df[,2], color = Participant_ID)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE) +
    labs(title = paste0(construct, " (r=", round(cor_val$estimate, 2), ")"),
         x = paste0("\u03BC", "EMA Variance"),
         y = "EMA Variance") +
    xlim(0, 1) +
    ylim(0, 1) +
    theme_bw() +
    theme(panel.background = element_rect(fill = "white")) +
    theme(legend.position = "none")
  return(plot)
}

```


Now, we will add all the plots into the list for each construct
```{r}

construct_plot_coded_list <- list()
for (construct in c("sad", "happy", "fatigue", "relax", "tense", "stress", "frust", "nervous", "focus", "control", "routine")) {
  construct_plot_coded_list[[construct]] <- construct_plot_coded(combined_df1, construct)
}


```

Now we will arrange them in a 3X4 grid using plot_grid
```{r}

construct_plots_coded_grid <- plot_grid(plotlist = construct_plot_coded_list, ncol = 4, nrow = 3, rel_heights = c(1, 1, 1))

```
Next, we can color code the scatter plots based on participant status. We will create a new construct_plot called construct_plot_coded_status where each point in the scatterplot will be color-coded based on the Participant.Status. We will not add the legend for color codes.

```{r}


construct_plot_coded_status_list <- list()
construct_plot_coded_status <- function(df, construct) {
  plot_df <- df %>% select(paste0("uema_", construct), paste0("ema_", construct), Participant.Status)
  plot_df <- plot_df[complete.cases(plot_df), ]
  cor_val <- cor.test(plot_df[,1], plot_df[,2], method="pearson")
  plot <- ggplot(plot_df, aes(x = plot_df[,1], y = plot_df[,2], color = Participant.Status)) +
    geom_point() +
    geom_smooth(method = "lm", se = FALSE) +
    labs(title = paste0(construct, " (r=", round(cor_val$estimate, 2), ")"),
         x = paste0("\u03BC", "EMA Variance"),
         y = "EMA Variance") +
    xlim(0, 1) +
    ylim(0, 1) +
    theme_bw() +
    theme(panel.background = element_rect(fill = "white")) +
    theme(legend.position = "none")
  return(plot)
}

```

Now, let's add them to the list and then render them using plot_grid
```{r}

construct_plot_coded_status_list <- list()
for (construct in c("sad", "happy", "fatigue", "relax", "tense", "stress", "frust", "nervous", "focus", "control", "routine")) {
  construct_plot_coded_status_list[[construct]] <- construct_plot_coded_status(combined_df1, construct)
}


```

Now let's display them in a 3X4 grid using plot_grid
```{r}

construct_plots_coded_status_grid <- plot_grid(plotlist = construct_plot_coded_status_list, ncol = 4, nrow = 3, rel_heights = c(1, 1, 1))

```
## Residual analysis using combined_df1
We will create a dataframe where each row has Participant_ID, and 11 columns for all the constructs. Each cell contains the residual value for that construct for that participant. We will use combined_df1 for this analysis.

```{r}

participant_ids <- combined_df1$Participant_ID

# Initialize residual_df with Participant_ID
residual_df <- data.frame(Participant_ID = participant_ids)

for (construct in c("sad", "happy", "fatigue", "relax", "tense", "stress", "frust", "nervous", "focus", "control", "routine")) {
  formula <- as.formula(paste0("ema_", construct, " ~ uema_", construct))
  lm_model <- lm(formula, data = combined_df1, na.action = na.exclude)
  residuals <- residuals(lm_model)
  
  # Ensure the residuals vector matches the number of rows in residual_df
  if (length(residuals) < nrow(residual_df)) {
    residuals <- c(residuals, rep(NA, nrow(residual_df) - length(residuals)))
  }
  
  # Add the residuals as a new column
  residual_df[[paste0("residual_", construct)]] <- residuals
}
```

### Plot residuals for each participant
Now we will plot residuals for each participant for each construct. For this, we will create a heatmap where the y axis is participant_ID and x-axis is the construct. The cell color will represent the residual value. The Participant_IDs will range from 1 to 174. This is so that the plot is clearly displayed.
```{r}


# Melt the residual_df
melted_residual <- melt(residual_df, id.vars = "Participant_ID")

# Change participant ID to number starting from 1
melted_residual$Participant_ID <- as.numeric(factor(melted_residual$Participant_ID))

# Create the heatmap
heatmap <- ggplot(melted_residual, aes(x = variable, y = Participant_ID, fill = value)) +
  geom_tile() +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  labs(title = "Heatmap of Variables by Participant ID",
       fill = "Value")


```

## Summarise residual analysis for combined_df1
We will create a summary table that shows the mean and standard deviation of residuals for each construct. We will use combined_df1 for this analysis.

```{r}

residual_summary_df <- data.frame()

## Compute residual summary for each construct
for (construct in c("sad", "happy", "fatigue", "relax", "tense", "stress", "frust", "nervous", "focus", "control", "routine")) {
  residuals <- residual_df[[paste0("residual_", construct)]]
  mean_residual <- mean(residuals, na.rm = TRUE)
  sd_residual <- sd(residuals, na.rm = TRUE)
  
  residual_summary_df <- rbind(residual_summary_df, data.frame(construct = construct, mean_residual = mean_residual, sd_residual = sd_residual))
}

```

## Compute the mean of residual across all the constructs for each participant in the residual_df
We will compute the mean for each participant and save it in a datafra,me
```{r}

residual_df$mean_residual <- rowMeans(residual_df[, -1], na.rm = TRUE)

```

## Plot the mean residual for each participant
We will use ggplot2 to plot a histogram across participants for the mean residual. We will also add a vertical line at 0 to show the mean residual value.
```{r}

mean_residual_plot <- ggplot(residual_df, aes(x = mean_residual)) +
  geom_histogram(bins = 30, fill = "steelblue", color = "white") +
  geom_vline(xintercept = 0, color = "red", linetype = "dashed") +
  theme_minimal() +
  labs(title = "Histogram of Mean Residuals",
       x = "Mean Residual",
       y = "Count")

```

